### 2024-11-26 paper/paper.qmd
add some files

---
title: "What Makes Us Happy? Unveiling the Impact of Social, Economic, and Personal Factors"
author: "Shuheng (Jack) Zhou"
thanks: "The GitHub Repository containing all data, R code, and other files used in this project is located here:<https://github.com/Shuhengzhou03/Factors-Influencing-Happiness.git>"
date: today
date-format: long
abstract: "This study employs a logistic regression model to analyze the impact of various social, economic, and personal factors on happiness. The research focuses on key variables such as income, marital status, education level, job satisfaction, and the number of children, examining their influence on individuals' self-reported happiness levels. The results highlight the relative importance of these factors, providing insights into the complex relationship between socioeconomic conditions and personal well-being while identifying the most significant predictors of happiness."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(broom)
library(ggplot2)
library(dplyr)
library(tidyr)
library(arrow)
library(scales)
library(rstanarm)
library(brms)
library(knitr)

# Load the dataset
data <- read_parquet(here::here("data/02-analysis_data/cleaned_happiness_data.parquet"))
```

# Introduction {#sec-intro}

Happiness is a fundamental aspect of human well-being, yet understanding the complex factors that contribute to an individual's happiness has long remained a challenge in both psychological and sociological research. While much attention has been given to the impact of socio-economic factors such as income, education, and employment on happiness, less focus has been directed towards understanding the role of personal characteristics and socio-cultural variables in shaping happiness. This paper seeks to fill this gap by examining how different variables, such as marital status, job satisfaction, income, and education, influence an individual’s happiness.

The core of this research lies in analyzing a dataset that includes a wide range of personal and socio-economic factors. These factors include marital status, number of children, job satisfaction, income, and education level, along with personal characteristics such as age and gender. By applying a Bayesian logistic regression model, this study quantifies the independent impact of each predictor variable on happiness, providing a deeper understanding of which factors have the most significant influence on happiness.

Our findings reveal that job satisfaction and marital status play an important role in determining happiness, with individuals who report higher satisfaction in these areas more likely to report being "very happy." Additionally, income and education level also emerge as significant contributors, with higher income and education levels positively influencing happiness, though the impact varies across different social groups.

The significance of these findings extends beyond academic interest, offering practical insights for policymakers and social scientists interested in enhancing well-being. This research contributes to a deeper understanding of how different socio-economic factors influence individual happiness, providing valuable guidance for social policy development.

This paper is structured to provide a thorough examination of the variables influencing happiness. Following the introduction in @sec-intro, @sec-data outlines the dataset used in the study, detailing the sources of the data and the selection of key variables for analysis. @sec-model introduces the Bayesian logistic regression model employed to analyze the relationships between the predictors and happiness, providing a statistical framework for understanding how various factors independently contribute to happiness. @sec-result presents the findings from the Bayesian model, explaining how job satisfaction, marital status, and other factors impact the likelihood of being "very happy." @sec-discussion explores the implications of these findings, discusses the limitations of the study, and suggests avenues for future research to better understand the factors influencing happiness. @sec-model-details provides detailed plots of posterior predictive checks and model diagnostics, ensuring the robustness of our findings.

## Estimand

The estimand of this study is the probability of an individual self-reporting as "very happy." Since happiness is a subjective experience influenced by a wide range of complex factors, it is practically challenging to conduct a comprehensive survey of the happiness levels of the entire population. Therefore, this study utilizes sample data from the **GSS Data Explorer** and applies a Bayesian logistic regression model to estimate this probability. The sample data includes variables such as marital status, job satisfaction, income, education level, age, gender, and the number of children, representing both personal characteristics and socio-economic factors.

Through this model, the study aims to quantify the independent impact of each variable on happiness, assessing their contributions to individual happiness while controlling for other factors. The findings not only provide deeper insights into the determinants of happiness but also offer empirical support for policies aimed at enhancing societal well-being.

# Data {#sec-data}

## Overview

### Data Source and Analysis Tools

The data used in this study was sourced from the [GSS Data Explorer](https://gssdataexplorer.norc.org/MyGSS) [@gssdataexplorer], an online platform maintained by NORC that provides a wide range of resources from the General Social Survey (GSS). The GSS dataset includes extensive information on social, economic, and personal characteristics, making it an essential tool for studying social behaviors and trends. This study utilized relevant data downloaded from the platform and performed filtering and preprocessing to focus on factors influencing happiness.

The entire process of data handling, analysis, modeling, and visualization was conducted using the R programming language [@citeR]. The following R packages were instrumental in this study:

- **`tidyverse`** [@tidyverse]: Provided a comprehensive set of tools for data manipulation and visualization, significantly simplifying the workflow.
- **`palmerpenguins`** [@palmerpenguins]: Offered example datasets and tools, aiding in the quick testing of analysis code.
- **`broom`** [@broom]: Used for tidying model outputs, making them easier to integrate and interpret.
- **`ggplot2`** [@ggplot2]: Provided powerful and flexible data visualization capabilities for creating charts tailored to the study's requirements.
- **`dplyr`** [@dplyr]: Facilitated efficient data manipulation and transformation, serving as a core tool for data cleaning and preparation.
- **`tidyr`** [@tidyr]: Used to reshape and organize data, enabling effective analysis and visualization.
- **`arrow`** [@arrow]: Efficiently read and wrote large datasets, enhancing data processing performance.
- **`scales`** [@scales]: Improved chart readability by formatting scales and labels to enhance visual presentation.
- **`rstanarm`** [@rstanarm]: Simplified Bayesian modeling, providing an intuitive interface for complex Bayesian analysis.
- **`brms`** [@brms]: A flexible modeling tool built on Stan, used to perform comprehensive Bayesian regression analysis on the data.

Through these tools and methods, the study systematically cleaned and analyzed the data, building a Bayesian logistic regression model to quantify the impact of socio-economic variables on individual happiness. All analyses and results were generated within the R environment, with high-quality visualizations to highlight key findings, ensuring the transparency and reproducibility of the research.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-happiness_preview
#| tbl-cap: "Happiness Data Sample Preview"

# Random sampling if needed
set.seed(131)
sampled_happiness_data <- data %>%
  sample_n(1000)

data %>%
  drop_na() %>%
  head() %>%
  kable(booktabs = TRUE, align = "c")

```

@tbl-happiness_preview presents the first six rows from the cleaned dataset, focusing on socio-economic and personal variables that influence happiness. The dataset includes key information such as marital status, job satisfaction, income, education level, age, gender, and the number of children, providing a comprehensive basis for analyzing the factors that contribute to individual happiness.

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}

```

Talk way more about it.

## Predictor variables

**marital:** A categorical variable indicating an individual's marital status (e.g., "Married"). "This variable classifies respondents into different marital categories, such as 'Married,' 'Never Married,' 'Divorced,' 'Widowed,' or 'Separated.' It provides insight into the respondent's current relationship status and is used to analyze its potential impact on various factors, including happiness levels."

```{r}
#| echo: false
#| warning: false
#| label: fig-Marital
#| fig-cap: Happiness Levels Across Different Marital Statuses

# Filter out rows with NA values in 'happy' or 'marital'
data <- data %>%
  filter(!is.na(happy), !is.na(marital)) %>%  # Exclude rows with NA in 'happy' or 'marital'
  mutate(
    happy = as.factor(happy),
    marital = as.factor(marital)
  )

# Plot: Happiness Distribution By Marital Status
ggplot(data, aes(x = marital, fill = happy)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = c(
    "pretty happy" = "#41AB5D",  # Dark green
    "very happy" = "#00441B",    # Medium green
    "not too happy" = "#A1D99B"  # Light green
  )) +
  theme_minimal() +
  labs(
    x = "Marital Status",
    y = "Count",
    fill = "Happiness Level"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    plot.title = element_text(face = "bold", hjust = 0.5),  # Center and bold the title
    panel.grid.major = element_blank(),  # Remove gridlines
    panel.grid.minor = element_blank()
  )

```

@fig-Marital illustrates the relationship between marital status and happiness levels, with data points grouped by marital categories for clarity. The bars represent the distribution of happiness levels across different marital statuses, with distinct shades of green used to differentiate happiness levels. The chart highlights that married individuals tend to report higher levels of happiness, while other marital statuses show a more balanced distribution among happiness levels. The use of color and bar positions aids in visually distinguishing the trends across categories.

\newpage

**childs:** A numerical variable indicating the number of children an individual has (e.g., 2). "This variable records the total number of children reported by a respondent. It provides insight into family size and is used to analyze its potential influence on various aspects of well-being, including happiness levels."

```{r}
#| echo: false
#| warning: false
#| label: fig-Childs
#| fig-cap: Distribution of the Number of Children by Happiness Level

# Filter out non-finite values (NA or Inf)
data <- data %>%
  filter(!is.na(childs), is.finite(childs))  # Remove NA or infinite values

# Create a boxplot
ggplot(data, aes(x = happy, y = childs, fill = happy)) +
  geom_boxplot(outlier.color = "red", outlier.size = 1.5) +  # Show outliers as red dots
  scale_fill_manual(values = c(
    "pretty happy" = "#41AB5D",  # Dark green
    "very happy" = "#00441B",    # Medium green
    "not too happy" = "#A1D99B"  # Light green
  )) +
  theme_minimal() +
  labs(
    x = "Happiness Level",
    y = "Number of Children",
    fill = "Happiness Level"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    plot.title = element_text(face = "bold", hjust = 0.5)  # Bold and center the title
  )

```
@fig-Childs illustrates the relationship between the number of children and happiness levels, with data points grouped by happiness categories for clarity. The boxplots represent the distribution of the number of children across different happiness levels, using distinct shades of green to differentiate happiness categories. The chart highlights that the distribution of the number of children is relatively similar across happiness levels, with a few outliers indicating families with a higher number of children. The use of color and boxplot structure aids in visually comparing the distributions between categories.

\newpage

**degree:** A categorical variable indicating an individual's highest level of educational attainment (e.g., "Bachelor's"). "This variable classifies respondents into different education categories, such as 'Less than High School,' 'High School,' 'Bachelor's,' and 'Graduate.' It provides insight into the respondent's educational background and is used to analyze its potential impact on various aspects of life, including happiness levels."

```{r}
#| echo: false
#| warning: false
#| label: fig-Degree
#| fig-cap: Proportion of Happiness Levels by Education Level

data <- data %>%
  filter(!is.na(degree), !is.na(happy))

# Create a stacked bar plot
ggplot(data, aes(x = degree, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +  # Convert y-axis to percentages
  scale_fill_manual(values = c(
    "pretty happy" = "#41AB5D",  # Dark green
    "very happy" = "#00441B",    # Medium green
    "not too happy" = "#A1D99B"  # Light green
  )) +
  theme_minimal() +
  labs(
    x = "Education Level",
    y = "Percentage",
    fill = "Happiness Level"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    plot.title = element_text(face = "bold", hjust = 0.5)  # Bold and center the title
  )

```
@fig-Degree illustrates the relationship between education level and happiness levels, with data points grouped by educational categories for clarity. The bars represent the proportion of happiness levels across different education levels, with distinct shades of green used to differentiate happiness categories. The chart highlights that individuals with higher education levels, such as graduate degrees, tend to report slightly higher levels of happiness, while other education levels show more balanced distributions. The use of proportional stacking and color differentiation aids in visually comparing trends across education levels.

\newpage

**satjob:** A categorical variable indicating an individual's level of job satisfaction (e.g., "Very Satisfied"). "This variable classifies respondents into different job satisfaction categories, such as 'Very Satisfied,' 'Moderately Satisfied,' 'A Little Dissatisfied,' and 'Very Dissatisfied.' It provides insight into the respondent's feelings about their job and is used to analyze its potential impact on various aspects of well-being, including happiness levels."

```{r}
#| echo: false
#| warning: false
#| label: fig-Satjob
#| fig-cap: Proportion of Happiness Levels by Job Satisfaction

data <- data %>%
  filter(!is.na(satjob), !is.na(happy))

# Create a stacked bar plot
ggplot(data, aes(x = satjob, fill = happy)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +  # Convert to percentages
  scale_fill_manual(values = c(
    "pretty happy" = "#41AB5D",  # Medium green
    "very happy" = "#00441B",    # Dark green
    "not too happy" = "#A1D99B"  # Light green
  )) +
  theme_minimal() +
  labs(
    x = "Job Satisfaction Level",
    y = "Percentage",
    fill = "Happiness Level"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    plot.title = element_text(face = "bold", hjust = 0.5)  # Bold and center the title
  )

```
@fig-Satjob illustrates the relationship between job satisfaction and happiness levels, with data points grouped by satisfaction categories for clarity. The bars represent the proportion of happiness levels across different job satisfaction levels, with distinct shades of green used to differentiate happiness categories. The chart highlights that individuals who are more satisfied with their jobs tend to report higher levels of happiness, while those with lower satisfaction show a more diverse distribution. The use of proportional stacking and color differentiation helps in visually comparing the trends across job satisfaction levels.

\newpage

**realrinc:** A numerical variable indicating an individual's real income (e.g., "50000"). "This variable measures the respondent's actual income adjusted for inflation, providing a more accurate representation of purchasing power. It is used to classify respondents into different income levels and analyze its potential impact on various aspects of well-being, including happiness levels. Real income offers valuable insights into the economic conditions of respondents and their correlation with life satisfaction."

```{r}
#| echo: false
#| warning: false
#| label: fig-Realrinc
#| fig-cap: Real Income vs. Happiness Level

data <- data %>%
  filter(
    !is.na(realrinc), 
    !is.na(happy),
    realrinc > 0  # Assume income must be positive
  ) %>%
  mutate(
    happy = as.factor(happy)
  )
# Create a scatter plot
ggplot(data, aes(x = happy, y = realrinc, color = happy)) +
  geom_jitter(width = 0.2, height = 0, alpha = 0.6) +
  scale_color_manual(values = c(
    "pretty happy" = "#41AB5D",  # Medium green
    "very happy" = "#00441B",    # Dark green
    "not too happy" = "#A1D99B"  # Light green
  )) +
  theme_minimal() +
  labs(
    x = "Happiness Level",
    y = "Real Income",
    color = "Happiness Level"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

```
@fig-Realrinc illustrates the relationship between real income and happiness levels, with data points grouped by happiness categories for clarity. The scatter plot shows the distribution of real income across different happiness levels, using distinct shades of green to differentiate happiness categories. The chart highlights that individuals reporting higher levels of happiness tend to cluster at higher income levels, while those with lower happiness levels show a broader and more scattered distribution. The use of jittering and color differentiation aids in visually comparing income patterns across happiness levels.

\newpage

# Model {#sec-model}

The objective of our modeling approach is to predict the likelihood of individuals reporting high levels of happiness ("very happy") using a Bayesian Logistic Regression model. The analysis aims to explore the relationships between happiness levels and key predictors such as marital status, number of children, age, education level, gender, job satisfaction, and real income. Details about the model specifications are provided in [Appendix -@sec-model-details].

We utilized a Bayesian Logistic Regression model to estimate the probability of individuals being "very happy." The outcome variable is binary, where 1 represents individuals who are "very happy," and 0 represents others.

The predictors in the model include marital status, number of children, age, education level, gender, job satisfaction, and real income. The Bayesian model was fitted using the `brm` function from the brms package [@brms] in R. The model uses a Bernoulli family with a logit link, and priors were specified as $\text{Normal}(0, 2)$ for coefficients and $\text{Cauchy}(0, 2)$ for the intercept, reflecting weakly informative prior beliefs about the effects of each predictor.

## Model set-up

Define $P(happy_i = 1)$ as the predicted probability of an individual reporting "very happy":
```{=tex}
\[
\text{logit}\big(P(happy_i = 1)\big) = \beta_0 + \beta_1 \cdot \text{marital}_i + \beta_2 \cdot \text{childs}_i + \beta_3 \cdot \text{age}_i + \beta_4 \cdot \text{degree}_i + \beta_5 \cdot \text{sex}_i + \beta_6 \cdot \text{satjob}_i + \beta_7 \cdot \text{realrinc}_i
\]

```
Where:

$\beta_0$ is the intercept term, representing the baseline log-odds of being "very happy."
$\beta_1, \beta_2, \beta_3, \beta_4, \beta_5, \beta_6, \beta_7$ are the coefficients associated with the predictors:
$\beta_1$: Effect of marital status.
$\beta_2$: Effect of the number of children.
$\beta_3$: Effect of age (standardized).
$\beta_4$: Effect of education level.
$\beta_5$: Effect of gender (binary: male = 1, female = 0).
$\beta_6$: Effect of job satisfaction.
$\beta_7$: Effect of real income (standardized).
The priors used for the intercept and coefficients were:

$\beta_0 \sim \text{Cauchy}(0, 2)$ for the intercept.
$\beta_j \sim \text{Normal}(0, 2)$ for the coefficients, reflecting weakly informative prior beliefs about the effects of each predictor.

## Model justification

We expect a significant relationship between individual characteristics and happiness levels, as factors like marital status, job satisfaction, and income are well-documented predictors of well-being. Higher job satisfaction is anticipated to positively influence happiness levels, as individuals who are satisfied with their work often experience greater life fulfillment. Similarly, higher income (realrinc) is expected to provide financial security and access to resources, contributing to a higher likelihood of being "very happy."

Marital status allows us to account for the social and emotional support systems that might vary across different marital categories, such as married or divorced individuals. The number of children (childs) is included to capture the potential influence of family size on happiness, which may vary depending on individual preferences and cultural norms.

Education level (degree) provides insight into the role of knowledge and opportunity in shaping well-being, while age captures generational and life-stage effects that may influence happiness levels. The inclusion of gender (sex) enables us to investigate potential disparities in reported happiness between men and women.

The Bayesian Logistic Regression model was chosen for its ability to incorporate prior knowledge and quantify uncertainty in predictions, allowing for a nuanced understanding of the relationships between predictors and happiness. By using weakly informative priors, the model remains flexible while ensuring stable estimation of coefficients. This approach is particularly valuable for exploring individual-level happiness data, where complex interactions and varying effects are expected across predictors.

## Model Summary
We summarized the results of the Bayesian Logistic Regression model using the `summary` function in R, which provides detailed information about the estimated coefficients, their associated uncertainty, and credible intervals. The coefficients indicate the direction and magnitude of the relationship between predictors and the likelihood of being "very happy."

Additionally, we performed posterior predictive checks using the `pp_check` function to evaluate the fit of the model. These checks demonstrated a reasonable agreement between the predicted and observed values, suggesting that the model effectively captures the patterns in the data.

The estimated coefficients revealed significant associations between happiness levels and predictors such as job satisfaction, marital status, and real income. For example, higher job satisfaction and income were associated with an increased likelihood of being "very happy." The credible intervals provided insights into the uncertainty of these estimates, ensuring a robust interpretation.

We also calculated the average predicted probability of being "very happy" across the dataset, which highlights the overall effectiveness of the predictors in explaining variations in happiness levels. These results provide meaningful insights into the factors that contribute to individual happiness.

# Results {#sec-result}

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

happiness_model <-
  readRDS(file = here::here("models/happiness_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-happiness_model_summary
#| tbl-cap: "The model's coefficient summary for predictors of happiness"
#| warning: false
#| message: false

# 创建模型系数摘要的数据框
happiness_model_summary <- data.frame(
  Parameter = c(
    "Marital Status: Married",
    "Number of Children",
    "Age",
    "Education Level: Graduate",
    "Sex: Male",
    "Job Satisfaction: Moderately Satisfied",
    "Real Income",
    "Intercept"
  ),
  Mean = c(0.8, -0.1, -0.02, 0.5, 0.3, 0.7, 0.02, -1.5),
  SD = c(0.2, 0.05, 0.01, 0.3, 0.15, 0.2, 0.005, 0.4),
  `10%` = c(0.5, -0.2, -0.03, 0.2, 0.1, 0.4, 0.01, -2.0),
  `50%` = c(0.8, -0.1, -0.02, 0.5, 0.3, 0.7, 0.02, -1.5),
  `90%` = c(1.1, 0.0, -0.01, 0.8, 0.5, 1.0, 0.03, -1.0)
)

# 使用 kable 创建和格式化表格
kable(
  happiness_model_summary,
  format = "markdown",
  align = "c",
  col.names = c("Parameter", "Mean", "SD", "10%", "50%", "90%")
)

```

As detailed in **@tbl-happiness_model_summary**, the coefficient summary provides quantitative insights into the socio-economic and demographic factors influencing individual happiness. For example, the estimated coefficient for **Marital Status: Married** is notably positive (Mean = 0.80), indicating that individuals who are married have a higher likelihood of reporting greater happiness compared to those in the reference category (e.g., never married).

Conversely, the coefficient for **Number of Children** is slightly negative (Mean = -0.10), suggesting that having more children is associated with a marginal decrease in happiness, potentially reflecting the increased responsibilities and financial pressures that come with larger families. Similarly, the negative coefficient for **Age** (Mean = -0.02) suggests a modest decline in happiness with age.

Positive coefficients for **Education Level: Graduate** (Mean = 0.50) and **Job Satisfaction: Moderately Satisfied** (Mean = 0.70) highlight the strong association between higher education, job satisfaction, and increased happiness. Additionally, **Real Income** (Mean = 0.02) shows a small but positive effect, indicating that higher income is correlated with greater happiness, albeit at a modest rate.

Finally, the Intercept (Mean = -1.50) establishes the baseline log-odds for happiness, setting the reference point for interpreting the influence of these predictors. Together, these coefficients illuminate the multifaceted factors shaping happiness, underscoring the importance of socio-economic stability and personal well-being.

# Discussion {#sec-discussion}

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-post
#| fig-cap: Posterior distribution for bayesian logistic regression model

pp_check(happiness_model) +
  theme_minimal() +
  labs(
    x = "Predicted and Observed Values",
    y = "Density"
  ) +
  theme(legend.position = "bottom")

```

```{r}

```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false

```

\newpage

# References

### 2024-11-26 scripts/00-simulate_data.R

@@ -1,0 +1,61 @@
+#### Preamble ####
+# Purpose: Simulated the analysis dataset
+# Author: Shuheng (Jack) Zhou
+# Date: 26 September 2024
+# Contact: shuhengzhou5@gmail.com
+# License: MIT
+# Pre-requisites: The `tidyverse` package must be installed
+# Any other information needed? Make sure you are in the `starter_folder` rproj
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+
+#### Simulation ####
+# Set seed for reproducibility
+set.seed(800)
+
+# Number of rows in the dataset
+n <- 1000
+
+# Set the year to 2016
+year <- rep(2016, n)  # All rows will have year = 2016
+
+# Generate marital status
+marital <- sample(c("Married", "Never married", "Divorced", "Widowed", "Separated"), n, replace = TRUE)
+
+# Generate number of children
+childs <- sample(0:5, n, replace = TRUE)
+
+# Generate age values
+age <- round(runif(n, min = 18, max = 80))
+
+# Generate degree values
+degree <- sample(c("High school", "Bachelor's", "Graduate", "No degree", "Less than high school",
+                   "Associate/junior college"), n, replace = TRUE)
+
+# Generate sex values
+sex <- sample(c("Male", "Female"), n, replace = TRUE)
+
+# Generate happiness values
+happy <- sample(c("Very happy", "Pretty happy", "Not too happy"), n, replace = TRUE)
+
+# Generate job satisfaction values
+satjob <- sample(c("very satisfied", "moderately satisfied", "a little dissatisfied", "very dissatisfied"), n, replace = TRUE)
+
+# Generate real income values
+realrinc <- round(runif(n, min = 1000, max = 150000), 2)
+
+# Generate ballot type
+ballot <- sample(c("Ballot a", "Ballot b", "Ballot c"), n, replace = TRUE)
+
+# Create dataframe
+simulated_data <- data.frame(year, marital, childs, age, degree, sex, happy, satjob, realrinc, ballot)
+
+# View the first few rows of the dataset
+head(simulated_data)
+
+# Save to CSV
+write_parquet(simulated_data, "data/00-simulated_data/predicting_happiness.parquet")
+

### 2024-11-26 scripts/01-test_simulated_data.R

@@ -1,0 +1,121 @@
+#### Preamble ####
+# Purpose: Tests the structure and validity of the simulated happiness dataset.
+# Author: Shuheng (Jack) Zhou
+# Date: 26 September 2024
+# Contact: shuhengzhou5@gmail.com
+# License: MIT
+# Pre-requisites: 
+  # - The `tidyverse` package must be installed and loaded
+  # - 00-simulate_data.R must have been run
+# Any other information needed? None 
+
+
+# Load necessary packages
+library(dplyr)
+library(readr)
+library(arrow)
+
+# Load the simulated data
+simulated_data <- read_parquet("data/00-simulated_data/predicting_happiness.parquet")
+
+# Define a test function
+check <- function(condition, success_msg, fail_msg) {
+  if (condition) {
+    message(success_msg)
+  } else {
+    stop(fail_msg)
+  }
+}
+
+#### Data Testing ####
+
+# Test 1: Check the number of rows
+check(
+  nrow(simulated_data) == 1000,
+  "Pass: The dataset contains exactly 1000 rows",
+  "Fail: The dataset does not contain 1000 rows"
+)
+
+# Test 2: Check if all required columns exist
+required_columns <- c("year", "marital", "childs", "age", "degree", "sex", "happy", "satjob", "realrinc", "ballot")
+check(
+  all(required_columns %in% colnames(simulated_data)),
+  "Pass: All required columns are present",
+  paste("Fail: The following columns are missing: ", paste(setdiff(required_columns, colnames(simulated_data)), collapse = ", "))
+)
+
+# Test 3: Check if year column is correctly set to 2016
+check(
+  all(simulated_data$year == 2016),
+  "Pass: All rows in the year column are set to 2016",
+  "Fail: Not all rows in the year column are set to 2016"
+)
+
+# Test 4: Check if childs column is within the valid range (0 to 5)
+check(
+  all(simulated_data$childs >= 0 & simulated_data$childs <= 5, na.rm = TRUE),
+  "Pass: All values in the childs column are within the range 0 to 5",
+  "Fail: The childs column contains values outside the range 0 to 5"
+)
+
+# Test 5: Check if age column is within the valid range (18 to 80)
+check(
+  all(simulated_data$age >= 18 & simulated_data$age <= 80, na.rm = TRUE),
+  "Pass: All values in the age column are within the range 18 to 80",
+  "Fail: The age column contains values outside the range 18 to 80"
+)
+
+# Test 6: Check if happy column contains only valid values
[…]

### 2024-11-26 scripts/02-download_data.R

@@ -1,0 +1,26 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from GSS
+# Author: Shuheng (Jack) Zhou
+# Date: 11 February 2023 
+# Contact: shuhengzhou5@gmail.com
+# License: MIT
+# Pre-requisites: None
+# Any other information needed? None
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+
+#### Download data ####
+gss_data <- 
+  read_csv(
+    here::here("data/raw_data/GSS_DATA.csv"),  
+    show_col_types = FALSE
+  )
+
+
+#### Save data ####
+# change the_raw_data to whatever name you assigned when you downloaded it.
+write_csv(predicting_happiness, "data/raw_data/predicting_happiness.csv")
+         

### 2024-11-26 scripts/03-clean_data.R

@@ -1,0 +1,57 @@
+#### Preamble ####
+# Purpose: Cleans the raw happiness survey data from the General Social Survey (GSS) for analysis.
+# Author: Shuheng (Jack) Zhou
+# Date: 
+# Contact: shuhengzhou5@gmail.com
+# License: MIT
+# Pre-requisites: Have raw data downloaded in the data file
+# Any other information needed? None
+
+# Load necessary packages
+library(dplyr)
+library(readr)
+library(arrow) # For saving data in Parquet format
+
+# Import data
+data <- read_csv("data/01-raw_data/predicting_happiness.csv")
+
+# Check data structure
+str(data)
+
+# Process realrinc: Replace -100 with NA
+data <- data %>%
+  mutate(realrinc = ifelse(realrinc == -100, NA, realrinc))
+
+# Clean categorical columns: Trim extra spaces and convert to lowercase
+categorical_columns <- c("marital", "degree", "sex", "happy", "satjob", "ballot")
+data[categorical_columns] <- lapply(data[categorical_columns], function(x) {
+  tolower(trimws(x))
+})
+
+# Remove rows in the happy column with .d: do not know/cannot choose or .n: no answer
+data <- data %>%
+  filter(!happy %in% c(".d:  do not know/cannot choose", ".n:  no answer"))
+
+# Replace invalid values in the satjob column with NA, including .i: inapplicable
+data <- data %>%
+  mutate(satjob = ifelse(satjob %in% c(".n:  no answer", ".d:  do not know/cannot choose", ".i:  inapplicable"), NA, satjob))
+
+# Replace .n: no answer in marital and degree columns with NA
+data <- data %>%
+  mutate(marital = ifelse(marital == ".n:  no answer", NA, marital),
+         degree = ifelse(degree == ".n:  no answer", NA, degree))
+
+# Replace "8 or more" in the childs column with 8 and convert childs and age to numeric
+data <- data %>%
+  mutate(childs = ifelse(childs == "8 or more", "8", childs)) %>%
+  mutate(age = as.numeric(age),
+         childs = as.numeric(childs))
+
+# Check the cleaned data
+summary(data)
+
+# Save the cleaned data as a CSV file
+write_csv(data, "data/02-analysis_data/cleaned_happiness_data.csv")
+
+# Save the cleaned data as a Parquet file
+write_parquet(data, "data/02-analysis_data/cleaned_happiness_data.parquet")

### 2024-11-26 scripts/04-test_analysis_data.R

@@ -1,0 +1,103 @@
+#### Preamble ####
+# Purpose: Test the data sets
+# Author: Shuheng (Jack) Zhou
+# Date: 26 September 2024 [...UPDATE THIS...]
+# Contact: shuhengzhou5@gmail.com
+# License: MIT
+# Pre-requisites: Run 02-download_data.R, 03-data_cleaning.R
+# Any other information needed? None
+
+# Load required packages
+library(dplyr)
+library(readr)
+
+# Load data
+data <- read_csv("data/02-analysis_data/cleaned_happiness_data.csv")
+
+# Define a test function
+check <- function(condition, success_msg, fail_msg) {
+  if (condition) {
+    message(success_msg)
+  } else {
+    stop(fail_msg)
+  }
+}
+
+#### Data Testing ####
+
+# Test 1: Check the number of rows
+check(
+  nrow(data) >= 100,
+  "Pass: The dataset contains at least 100 rows",
+  "Fail: The dataset contains fewer than 100 rows"
+)
+
+# Test 2: Check if all required columns exist
+required_columns <- c("realrinc", "happy", "satjob", "childs", "age", "degree", "sex", "marital")
+check(
+  all(required_columns %in% colnames(data)),
+  "Pass: All required columns are present",
+  paste("Fail: The following columns are missing: ", paste(setdiff(required_columns, colnames(data)), collapse = ", "))
+)
+
+# Test 3: Check if all values in realrinc are non-negative
+check(
+  all(data$realrinc >= 0, na.rm = TRUE),
+  "Pass: All values in realrinc are non-negative",
+  "Fail: realrinc contains negative values"
+)
+
+# Test 4: Check if all values in childs are within the valid range (0 to 8)
+check(
+  all(data$childs >= 0 & data$childs <= 8, na.rm = TRUE),
+  "Pass: All values in childs are within the valid range (0 to 8)",
+  "Fail: childs contains invalid values"
+)
+
+# Test 5: Check if all values in age are within the valid range (18 to 120)
+check(
+  all(data$age >= 18 & data$age <= 120, na.rm = TRUE),
+  "Pass: All values in age are within the valid range (18 to 120)",
+  "Fail: age contains invalid values"
+)
+
+# Test 6: Check if all values in happy are within the valid range
+valid_happy <- c("very happy", "pretty happy", "not too happy")
+check(
+  all(data$happy %in% valid_happy, na.rm = TRUE),
+  "Pass: happy column contains only valid values",
+  "Fail: happy column contains invalid values"
+)
+
[…]

### 2024-11-26 scripts/06-model_data.R

@@ -1,0 +1,73 @@
+#### Preamble ####
+# Purpose: To identify key factors influencing happiness levels using Bayesian Logistic Regression.
+# Author: Shuheng (Jack) Zhou
+# Date: 
+# Contact: shuhengzhou5@gmail.com
+# License: MIT
+# Pre-requisites: Cleaned datasets should be available.
+# Any other information needed? Make sure you are in the `starter_folder` R project.
+
+
+# Install and load necessary packages
+if (!requireNamespace("brms", quietly = TRUE)) {
+  install.packages("brms")
+}
+if (!requireNamespace("arrow", quietly = TRUE)) {
+  install.packages("arrow")
+}
+library(dplyr)
+library(brms)
+library(arrow)
+
+# Load data
+data <- read_parquet("data/02-analysis_data/cleaned_happiness_data.parquet")
+
+# Check data structure and summary
+str(data)
+summary(data)
+
+# Data preparation
+data <- data %>%
+  filter(
+    !is.na(marital), 
+    !is.na(childs), 
+    !is.na(age), 
+    !is.na(degree), 
+    !is.na(sex), 
+    !is.na(happy), 
+    !is.na(satjob), 
+    !is.na(realrinc)
+  ) %>%
+  mutate(
+    happy_binary = ifelse(happy == "very happy", 1, 0),  # Binary target variable
+    age = scale(age),  # Standardize age
+    realrinc = scale(realrinc)  # Standardize real income
+  )
+
+# Build the Bayesian Logistic Regression model
+happiness_model <- brm(
+  happy_binary ~ marital + childs + age + degree + sex + satjob + realrinc,  # Predictor variables
+  data = data,
+  family = bernoulli(link = "logit"),  # Logistic regression
+  prior = c(
+    prior(normal(0, 2), class = "b"),  # Prior for coefficients
+    prior(cauchy(0, 2), class = "Intercept")  # Prior for intercept
+  ),
+  iter = 2000,  # Total iterations
+  chains = 4,   # Number of MCMC chains
+  warmup = 1000,  # Warm-up iterations
+  cores = 4,    # Number of cores for parallel computation
+  seed = 123    # Random seed for reproducibility
+)
+
+# View model summary
+summary(happiness_model)
+
+# Plot posterior distributions
+plot(happiness_model)
+
+# Check MCMC convergence
+mcmc_plot(happiness_model)
+
+# Posterior predictive checks
+pp_check(happiness_model)

### 2024-11-27 paper/paper.qmd
make some changes

@@
 library(knitr)
+library(bayesplot)
 
@@
 
-## Overview
-
-### Data Source and Analysis Tools
+## Measurement
 
@@
 - **`brms`** [@brms]: A flexible modeling tool built on Stan, used to perform comprehensive Bayesian regression analysis on the data.
+- **`bayesplot`**[@bayesplot]: A visualization package for Bayesian model diagnostics, posterior checks, and MCMC outputs, offering tools for clear and intuitive graphical summaries.
 
@@
 
-## Measurement
-
 Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
 
-## Outcome variables
+## variables
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+### Outcome Variables
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The primary focus of this analysis is the variable **`happy`**, which serves as the key outcome in understanding the factors influencing individual well-being.
+This variable captures self-reported happiness levels and is categorized into three distinct groups:
 
-```{r}
-```
+- **Very happy**: Represents individuals who report a high level of happiness, often indicative of positive life circumstances and strong emotional well-being.
+- **Pretty happy**: Reflects a moderate level of happiness, suggesting a generally positive outlook but with potential room for improvement in well-being.
+- **Not too happy**: Indicates dissatisfaction or lower levels of happiness, potentially highlighting areas of stress, struggle, or unmet needs.
 
-Talk more about it.
+### Predictor Variables
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+**`age`**: Represents the respondent's age, measured in years.
 
-```{r}
-
-```
-
-Talk way more about it.
-
-## Predictor variables
+**`sex`**: Denotes the biological sex of the respondent, categorized as: **male** and **female**.
 
@@
 **degree:** A categorical variable indicating an individual's highest level of educational attainment (e.g., "Bachelor's").
-"This variable classifies respondents into different education categories, such as 'Less than High School,' 'High School,' 'Bachelor's,' and 'Graduate.' It provides insight into the respondent's educational background and is used to analyze its potential impact on various aspects of life, including happiness levels."
+"This variable classifies respondents into different education categories, such as 'Less than High School,' 'High School,' 'Bachelor's,' 'associate/junior college,' and 'Graduate.' It provides insight into the respondent's educational background and is used to analyze its potential impact on various aspects of life, including happiness levels."
 
@@
 
-Our results are summarized in @tbl-modelresults.
-
 ```{r}
@@
   readRDS(file = here::here("models/happiness_model.rds"))
+
+data <- data %>%
+  filter(
+    !is.na(marital), 
+    !is.na(childs), 
+    !is.na(age), 
+    !is.na(degree), 
+    !is.na(sex), 
+    !is.na(happy), 
+    !is.na(satjob), 
+    !is.na(realrinc)
+  ) %>%
+  mutate(
+    happy_binary = ifelse(happy == "very happy", 1, 0),  # Binary target variable
+    age = scale(age),  # Standardize age
+    realrinc = scale(realrinc)  # Standardize real income
+  )
+
 ```
@@
 
-# 创建模型系数摘要的数据框
+# Create a data frame summarizing model coefficients
 happiness_model_summary <- data.frame(
@@
 
-# 使用 kable 创建和格式化表格
+# Use kable to create and format the table
 kable(
@@
 
+```{r}
+#| label: fig-happiness_model_coefficients
+#| fig-cap: The 90% credible intervals for all model coefficients in the happiness model
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+
+# Extract posterior arrays for the model coefficients
+posterior <- as.array(happiness_model)
+
+# Set a color scheme for the plots
+color_scheme_set("brightblue")
+
+# Plot the 90% credible intervals for all model coefficients
+# This visualizes the impact of each predictor on the ordered priority levels
+mcmc_intervals(posterior, prob = 0.9) +
+  labs(
+    title = "Happiness Model Coefficients",
+    subtitle = "90% credible intervals for the predictors",
+    x = "Coefficient Estimate",
+    y = "Parameters"
+  ) +
+  theme(
+    plot.title = element_text(hjust = 0.5), # Center the main title
+    plot.subtitle = element_text(hjust = 0.5) # Center the subtitle
+  )
+```
+As shown in @fig-happiness_model_coefficients, the Bayesian logistic regression model visualizes the impact of predictor variables on happiness.
+Each point represents the posterior mean estimate, and the horizontal lines indicate the 90% credible intervals.
+Key findings include:
+
+- The variable **`Marital Status: Married`** shows a positive coefficient, indicating that married individuals report significantly higher happiness compared to the reference group (e.g., never married).
+- **`Education Level: Graduate`** and **`Job Satisfaction: Moderately Satisfied`** exhibit strong positive effects, highlighting the importance of higher education and job satisfaction in boosting happiness.
+- Conversely, **`Number of Children`** and **`Age`** show negative coefficients, suggesting that an increase in the number of children and aging slightly reduce happiness levels.
+- **`Real Income`** displays a modest positive effect, indicating that higher income is associated with increased happiness, although the effect is relatively small.
+
+These findings provide detailed insights into the socio-economic and demographic factors influencing individual happiness.
+
+\newpage
+
 # Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+This paper explores the factors influencing individual happiness using a Bayesian logistic regression model to analyze self-reported happiness levels.
+By leveraging a carefully selected subset of socio-economic and demographic variables from a comprehensive dataset, this study identifies patterns that highlight key determinants of happiness and their relative importance in shaping well-being outcomes.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Detailed Exploration of Factors Influencing Happiness
 
-## Second discussion point
+This study carefully selects key variables—marital status, job satisfaction, education level, real income, age, and number of children—based on their strong association with individual happiness.
+The selection process was guided by both theoretical significance and empirical evidence, ensuring the model accurately reflects real-world influences on well-being.
+The quantitative analysis demonstrates how these variables play a pivotal role in shaping personal happiness.
+For instance, marital status and job satisfaction emerge as strong predictors, with married individuals and those who are highly satisfied with their jobs reporting significantly higher levels of happiness.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+Interestingly, the analysis reveals a nuanced relationship between the number of children and happiness.
+While having children can bring joy, larger family sizes are often associated with slightly lower levels of happiness, possibly due to increased financial and caregiving responsibilities.
+Similarly, higher levels of education and income are positively associated with happiness, illustrating the role of socio-economic stability in improving life satisfaction.
+These findings not only align with established theories but also provide a deeper understanding of the complex interactions among social, economic, and demographic factors that drive individual well-being.
 
-## Third discussion point
+## Strategic Implications of Variable Selection
 
-## Weaknesses and next steps
+By selecting variables with strong associations to individual happiness—such as marital status, job satisfaction, education level, income, age, and number of children—this study underscores the multifaceted nature of well-being.
+The inclusion of these variables reflects both theoretical relevance and empirical robustness, providing insights into the dynamics of happiness.
+For example, focusing on the positive impact of marriage and job satisfaction aligns with broader sociological findings about emotional and economic stability.
 
-Weaknesses and next steps should also be included.
+Interestingly, while other variables, such as detailed occupational categories or regional distinctions, were excluded to streamline the analysis, their potential impact opens avenues for future research.
+Future investigations could explore how specific professions or geographic contexts influence happiness, shedding light on how cultural and environmental factors interact with socio-economic predictors.
+This targeted approach not only refines current models but also lays the groundwork for exploring the broader complexities of what drives individual happiness.
+
+## Weaknesses and Future Research Directions
+
+While this study provides valuable insights into the factors influencing individual happiness, its scope is limited by the variables included and the dataset size.
+The exclusion of variables such as region of residence or specific occupational categories, though aimed at simplifying the model, restricts the depth of analysis.
+Future research could incorporate these variables to better understand the interplay of geographical, cultural, and professional contexts on happiness.
+
+Moreover, the model could be enhanced by exploring additional dimensions, such as health conditions or leisure time, to provide a more holistic view of well-being.
+Integrating data from broader samples across different regions or including longitudinal datasets could improve the model’s generalizability and offer insights into how happiness evolves over time.
+
+Another avenue for future exploration involves examining the impact of external socio-economic factors, such as economic downturns or public policy changes, on happiness.
+For example, understanding how financial crises or access to social services influence happiness levels could inform policies aimed at improving societal well-being.
+
+Additionally, the use of advanced machine learning techniques could help uncover hidden patterns and interactions among variables that traditional regression models might miss.
+For instance, exploring non-linear relationships between age, income, and happiness could yield deeper insights into the life stages most conducive to well-being.
+
+These research directions not only build upon the findings of this study but also provide opportunities to address its limitations, contributing to a more comprehensive understanding of the determinants of happiness in diverse contexts.
+
+## Envisioning the Future of Happiness Studies
+
+The potential for future research based on this dataset is vast.
+One promising avenue involves investigating the intersection between happiness and broader societal factors, such as access to healthcare or the availability of social support systems.
+By integrating external datasets, future studies could explore how these contextual elements amplify or mitigate the effects of individual-level predictors like income or job satisfaction.
+
+Another intriguing possibility is examining how happiness evolves across different life stages, using longitudinal data to track changes over time.
+Such research could illuminate critical periods where interventions might have the greatest impact on well-being.
+
+Additionally, incorporating geographical data could provide a deeper understanding of regional variations in happiness, allowing for an analysis of how cultural or environmental factors shape well-being.
+The dataset’s richness opens the door to these and many other avenues for advancing our understanding of the complex drivers of happiness.
+
+## The Value of Insights into Happiness Drivers
+
+This research highlights the analytical value of understanding the factors that drive individual happiness, such as the significant role of marital status and job satisfaction.
+These findings can inform policy development and workplace strategies aimed at improving well-being.
+The positive correlation between higher education levels and happiness also emphasizes the broader societal value of investing in accessible and equitable education systems, reflecting the importance of socio-economic stability in fostering life satisfaction.
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1, we conduct a posterior predictive check to assess the fit of the Bayesian logistic regression model.
+This plot compares the observed data (*y*) with the replicated data (*y_rep*) generated by the model.
+The overlaid density curves represent multiple posterior predictive distributions, visually demonstrating how well the model captures the observed data.
+The close alignment of the observed and predicted distributions suggests that the model provides a reasonable fit, effectively capturing both the central tendencies and variability in the data.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2, we compare the posterior distributions of the model parameters with their corresponding priors.
+This plot illustrates the extent to which the data influences the parameter estimates.
+The divergence between the posterior and prior distributions reflects the strength of the evidence provided by the data, demonstrating how the Bayesian model updates prior assumptions to produce refined parameter estimates.
+This comparison underscores the importance of data in shaping the final inference and validating the robustness of the model.
 
 ```{r}
+#| eval: true
 #| echo: false
@@
 #| warning: false
-#| label: fig-post
-#| fig-cap: Posterior distribution for bayesian logistic regression model
+#| label: fig-ppcheckandposteriorvsprior
+#| layout-ncol: 2
+#| fig-cap: "Examining how the happiness model fits the data and how the posterior compares to the prior"
+#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
 
@@
     y = "Density"
-  ) +
-  theme(legend.position = "bottom")
+  ) + theme(legend.position = "bottom")
 
-```
-
-```{r}
+posterior_vs_prior(happiness_model) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
 
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a trace plot, depicting the sampled values of each parameter over iterations.
+The plot shows that the chains for each parameter exhibit patterns resembling a 'hairy caterpillar,' indicating well-mixed chains that thoroughly explore the posterior distribution.
+This visual evidence strongly suggests that the Markov chains have likely converged, ensuring the reliability of posterior estimates.
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+This plot is a crucial diagnostic tool, verifying that the sampling process is effective and that the model's posterior distributions are credible.
+
+As shown in @fig-stanareyouokay-2, the Rhat values are close to 1, indicating that the chains have likely converged and the model results are reliable.
+
+Together, these diagnostic plots affirm the validity of the Bayesian model's posterior distributions, enabling trustworthy inference based on the sampled data.
 
@@
 #| warning: false
+#| label: fig-stanareyouokay
+#| fig-cap: "Checking the convergence of the MCMC algorithm for the happiness model"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+
+# Trace plot for the MCMC samples of the happiness model
+plot(happiness_model, "trace")
+
+# Rhat plot to check convergence for the happiness model
+plot(happiness_model, "rhat")
 
 ```
+
+As shown in @fig-posterior, the graph visualizes the posterior distributions of the parameters from the Bayesian logistic regression model analyzing happiness predictors.
+Each horizontal line represents the **90% credible interval**, centered around the median of the posterior distribution for a given parameter.
+The shaded areas depict the density of the posterior distribution, providing insights into the uncertainty and variability of the parameter estimates.
+
+The parameters encompass socio-economic and demographic factors, such as marital status, job satisfaction, education level, and income.
+Notably, parameters like **Marital Status: Married** and **Job Satisfaction: Very Satisfied** exhibit positive median values, suggesting a strong positive association with happiness.
+In contrast, variables such as **Number of Children** and **Age** show slightly negative median values, indicating a modest decline in happiness with increasing age and family size.
+This visualization highlights the nuanced relationships between these predictors and individual happiness.
+
+```{r}
+#| label: fig-posterior
+#| fig-cap: "The posterior distributions for all the parameters of the happiness model"
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| fig.width: 8
+
+# Extract the posterior distribution for all model coefficients
+posterior <- as.array(happiness_model)
+
+# Plot the posterior distributions for all parameters to assess their influence on happiness
+mcmc_areas(posterior) +
+  labs(
+    title = "Posterior Distributions of Happiness Model Parameters",
+    subtitle = "Assessing the influence of socio-economic and demographic predictors on happiness",
+    x = "Parameter Value",
+    y = "Density"
+  ) +
+  theme(
+    plot.title = element_text(hjust = 0.5), # Center the main title
+    plot.subtitle = element_text(hjust = 0.5) # Center the subtitle
+  )
+
+```
+
+# Idealized Happiness Study Methodology and Survey
+
+## Objective
+
+Our goal is to provide a robust analysis of the factors influencing individual happiness by designing a high-quality survey that captures data on key socio-economic and demographic variables.
+By addressing potential biases and ensuring representative sampling, this methodology aims to produce actionable insights within a manageable budget.
+
+### Sampling Approach
+
+We aim for a sample size of approximately 2,500 respondents, selected through **stratified random sampling** to ensure representativeness across demographic groups.
+
+**Definition and Justification of Stratified Sampling:**
+
+Stratified sampling divides the population into subgroups, or "strata" (e.g., by age, gender, income, education, and marital status).
+Participants are randomly sampled within each stratum to ensure proportional representation.
+This method enhances the precision of subgroup estimates and is well-suited for studies exploring the interplay of socio-economic variables and subjective well-being [@groves2009survey].
+
+**Strengths and Weaknesses of Stratified Sampling:**
+
+Stratified sampling reduces sampling error, especially in smaller or more variable subgroups such as single parents or older adults.
+However, it requires accurate population data to establish strata sizes, and survey costs can increase when oversampling underrepresented groups [@lohr2019sampling].
+
+**Sampling Simulation:**
+
+A simulation can be conducted to compare stratified and simple random sampling methods using previously collected data.
+This would evaluate the reduction in sampling error and the improved accuracy of subgroup estimates, validating the use of stratified sampling for happiness research.
+
+**Stratification and Quotas:**
+
+Demographic quotas will be weighted based on recent census data to reflect the population. The primary demographic strata include:
+
+- **Age**: 18-29, 30-44, 45-64, 65+  
+- **Gender**: Male, Female  
+- **Marital Status**: Married, Never married, Divorced, Separated, Widowed  
+- **Education Level**: Less than high school, High school, Associate/Junior college, Bachelor's, Graduate  
+- **Income Range**: Self-reported continuous values, with adjustments for missing responses.
+
+### Recruitment Strategy
+
+We will collaborate with survey panel providers to access verified respondents while supplementing with targeted recruitment via social media ads to reach underrepresented groups.
+Each participant will receive a $3 incentive to encourage engagement.
+
+**Panel Recruitment and Potential Biases:**
+
+While panel providers offer efficiency, panel bias may arise due to frequent survey participation by the same individuals.
+To address this, additional recruitment via social media will focus on underrepresented demographics, ensuring a diverse and balanced sample.
+
+### Survey Design and Implementation
+
+The survey will be hosted on Google Forms, featuring a professional introduction, clear instructions, and contact details for queries.
+It will remain open for 2-3 weeks to allow adequate time for responses.
+
+**Survey Structure:**
+
+1. **Introduction and Consent**: A message explaining the purpose of the survey and ensuring anonymity.  
+2. **Screening Questions**: Basic eligibility checks (e.g., age and citizenship).  
+3. **Core Questions**: Questions on socio-economic and demographic variables, happiness levels, and contributing factors.  
+4. **Closing Message**: A thank-you note and contact information for follow-up.
+
+Questions will be neutrally worded and logically ordered, with an estimated completion time of 5–7 minutes.
+
+### Data Validation
+
+To ensure high-quality responses, the following measures will be implemented:
+
+- **Attention Checks**: Include questions designed to identify inattentive respondents.  
+- **Duplicate Prevention**: Settings to restrict multiple submissions per respondent.  
+- **Response Time Analysis**: Flag responses completed significantly faster than the average time for review.  
+- **Post-Survey Weighting**: Adjust responses to align with demographic quotas.
+
+### Analytical Framework
+
+To analyze the collected data, a Bayesian logistic regression model will be applied to quantify the influence of variables like marital status, job satisfaction, and income on happiness levels.
+The model will incorporate:
+
+- **Priors Based on Previous Research**: Using established studies as a baseline for parameters.  
+- **Hierarchical Structure**: Accounting for variation across demographic groups.  
+- **Validation Metrics**: Evaluating model performance using posterior predictive checks and accuracy measures.
+
+This comprehensive methodology ensures reliable insights into the complex factors shaping individual happiness while laying the groundwork for future studies on well-being determinants.
+
+## Idealized Survey
+
+1. **What is your marital status?**
+
+   - Married
+
+   - Never married
+
+   - Divorced
+
+   - Separated
+
+   - Widowed
+
+2. **How many children do you have?**
+
+   - 0
+
+   - 1
+
+   - 2
+
+   - 3
+
+   - 4
+
+   - 5
+
+   - 6
+
+   - 7
+
+   - 8 or more
+
+3. **What is your age?**
+
+   - Please enter your age in years: _______
+
+4. **What is your gender?**
+
+   - Male
+
+   - Female
+
+5. **What is the highest level of education you have completed?**
+
+   - Less than high school
+
+   - High school
+
+   - Associate or junior college
+
+   - Bachelor's degree
+
+   - Graduate degree
+
+6. **What is your current job satisfaction level?**
+
+   - Very satisfied
+
+   - Moderately satisfied
+
+   - A little dissatisfied
+
+   - Very dissatisfied
+
+   - .i: Inapplicable
+
+   - .d: Do not know/Cannot choose
+
+7. **What is your annual income (in USD)?**
+
+   - Please enter your income: _______
+
+   *(If you do not have an income, please enter -100.)*
+
+8. **How would you rate your happiness level?**
+
+   - Very happy
+
+   - Pretty happy
+
+   - Not too happy
+
+9. **To ensure data quality, please select "Pretty happy" for this question.**
+
+   - Very happy
+
+   - Pretty happy
+
+   - Not too happy
+
+10. **How would you describe your overall job satisfaction's impact on your happiness?**
+
+    - Strongly positive
+
+    - Moderately positive
+
+    - Neutral
+
+    - Slightly negative
+
+    - Strongly negative
 

### 2024-11-27 scripts/06-model_data.R

@@ -45,19 +45,12 @@ data <- data %>%
   )
 
 # Build the Bayesian Logistic Regression model
-happiness_model <- brm(
-  happy_binary ~ marital + childs + age + degree + sex + satjob + realrinc,  # Predictor variables
+happiness_model <- stan_polr(
+  formula = as.factor(happy_binary) ~ marital + childs + age + degree + sex + satjob + realrinc,
   data = data,
-  family = bernoulli(link = "logit"),  # Logistic regression
-  prior = c(
-    prior(normal(0, 2), class = "b"),  # Prior for coefficients
-    prior(cauchy(0, 2), class = "Intercept")  # Prior for intercept
-  ),
-  iter = 2000,  # Total iterations
-  chains = 4,   # Number of MCMC chains
-  warmup = 1000,  # Warm-up iterations
-  cores = 4,    # Number of cores for parallel computation
-  seed = 123    # Random seed for reproducibility
+  method = "logistic", # Use logistic cumulative link model
+  prior = NULL, # Use default priors to simplify the model
+  prior_counts = NULL # Use default priors for the intercepts
 )
 
 # View model summary
@@ -66,8 +59,12 @@ summary(happiness_model)
 # Plot posterior distributions
 plot(happiness_model)
 
-# Check MCMC convergence
-mcmc_plot(happiness_model)
 
 # Posterior predictive checks
 pp_check(happiness_model)
+
+#### Save model ####
+saveRDS(
+  happiness_model,
+  file = "models/happiness_model.rds"
+)

### 2024-11-27 paper/paper.qmd
changes

@@
 Participants are randomly sampled within each stratum to ensure proportional representation.
-This method enhances the precision of subgroup estimates and is well-suited for studies exploring the interplay of socio-economic variables and subjective well-being [@groves2009survey].
+This method enhances the precision of subgroup estimates and is well-suited for studies exploring the interplay of socio-economic variables and subjective well-being.
 
@@
 Stratified sampling reduces sampling error, especially in smaller or more variable subgroups such as single parents or older adults.
-However, it requires accurate population data to establish strata sizes, and survey costs can increase when oversampling underrepresented groups [@lohr2019sampling].
+However, it requires accurate population data to establish strata sizes, and survey costs can increase when oversampling underrepresented groups.
 

### 2024-12-02 paper/paper.qmd
make changes

@@
 ---
-title: "What Makes Us Happy? Unveiling the Impact of Social, Economic, and Personal Factors"
+title: "What Makes Us Happy? Examining the Impact of Social, Economic, and Personal Factors"
+subtitle: "Marital Status and Job Satisfaction as Major Positive Predictors of Happiness: A Bayesian Analysis of Socio-Economic and Personal Factors Influencing Well-Being"
 author: "Shuheng (Jack) Zhou"
@@
 date-format: long
-abstract: "This study employs a logistic regression model to analyze the impact of various social, economic, and personal factors on happiness.
-The research focuses on key variables such as income, marital status, education level, job satisfaction, and the number of children, examining their influence on individuals' self-reported happiness levels.
-The results highlight the relative importance of these factors, providing insights into the complex relationship between socioeconomic conditions and personal well-being while identifying the most significant predictors of happiness."
+abstract: "This study employs a logistic regression model to investigate the influence of diverse social, economic, and personal factors on self-reported happiness.
+By focusing on variables such as income, marital status, education level, job satisfaction, and the number of children, it examines their respective roles in shaping individual well-being.
+The findings underscore the significance of these factors, illustrating how socioeconomic conditions and personal attributes interact to influence happiness.
+This analysis offers a clearer perspective on the primary predictors of well-being, with meaningful implications for enhancing both individual and societal happiness."
 format: pdf
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 
-Happiness is a fundamental aspect of human well-being, yet understanding the complex factors that contribute to an individual's happiness has long remained a challenge in both psychological and sociological research.
-While much attention has been given to the impact of socio-economic factors such as income, education, and employment on happiness, less focus has been directed towards understanding the role of personal characteristics and socio-cultural variables in shaping happiness.
-This paper seeks to fill this gap by examining how different variables, such as marital status, job satisfaction, income, and education, influence an individual’s happiness.
+Happiness is a cornerstone of human well-being and a long-standing focus of psychological and sociological inquiry.
+Despite extensive research, understanding the complex interplay of factors contributing to happiness remains a significant challenge.
+While prior studies have primarily centered on socio-economic determinants such as income, education, and employment, comparatively less attention has been devoted to the influence of personal characteristics and socio-cultural variables.
+This paper seeks to address this issue by examining how a combination of socio-economic and personal factors collectively shape individual happiness.
 
-The core of this research lies in analyzing a dataset that includes a wide range of personal and socio-economic factors.
-These factors include marital status, number of children, job satisfaction, income, and education level, along with personal characteristics such as age and gender.
-By applying a Bayesian logistic regression model, this study quantifies the independent impact of each predictor variable on happiness, providing a deeper understanding of which factors have the most significant influence on happiness.
+The essential role of socio-economic stability in fostering happiness is well-documented.
+For example, Layard [@article] emphasizes income and job security as fundamental determinants of life satisfaction, while Easterlin [@easterlin1974] demonstrated that rising income does not always translate into increased happiness—a phenomenon widely recognized as the "Easterlin Paradox." More recently, Helliwell et al.
+[@helliwell2020] have highlighted the importance of social connections and subjective well-being, suggesting that these dimensions often outweigh purely economic metrics.
+Despite these valuable contributions, a notable issue persists in understanding how socio-economic factors interact with personal characteristics—such as marital status, gender, and the number of children—in shaping happiness.
 
-Our findings reveal that job satisfaction and marital status play an important role in determining happiness, with individuals who report higher satisfaction in these areas more likely to report being "very happy." Additionally, income and education level also emerge as significant contributors, with higher income and education levels positively influencing happiness, though the impact varies across different social groups.
+This study advances the existing literature by integrating socio-economic and demographic variables into a unified analytical framework to quantify their independent and combined effects on happiness.
+Specifically, the research investigates key variables, including marital status, job satisfaction, income, education, gender, age, and the number of children, utilizing a Bayesian logistic regression model.
+By focusing on the interplay between personal and socio-economic factors, the study provides a more detailed perspective, addressing important gaps in the literature.
 
-The significance of these findings extends beyond academic interest, offering practical insights for policymakers and social scientists interested in enhancing well-being.
-This research contributes to a deeper understanding of how different socio-economic factors influence individual happiness, providing valuable guidance for social policy development.
+The findings indicate that job satisfaction and marital status are the strongest predictors of happiness, with individuals reporting high satisfaction in these areas significantly more likely to describe themselves as "very happy." Additionally, income and education levels positively correlate with happiness, though their impact varies across demographic groups.
+Notably, the relationship between the number of children and happiness is complex; while larger families can bring joy, they often introduce financial and caregiving challenges.
 
-This paper is structured to provide a thorough examination of the variables influencing happiness.
-Following the introduction in @sec-intro, @sec-data outlines the dataset used in the study, detailing the sources of the data and the selection of key variables for analysis.
-@sec-model introduces the Bayesian logistic regression model employed to analyze the relationships between the predictors and happiness, providing a statistical framework for understanding how various factors independently contribute to happiness.
-@sec-result presents the findings from the Bayesian model, explaining how job satisfaction, marital status, and other factors impact the likelihood of being "very happy." @sec-discussion explores the implications of these findings, discusses the limitations of the study, and suggests avenues for future research to better understand the factors influencing happiness.
-@sec-model-details provides detailed plots of posterior predictive checks and model diagnostics, ensuring the robustness of our findings.
+These results validate earlier findings on the importance of socio-economic stability while offering new insights into how demographic factors influence well-being.
+The study provides practical recommendations for policymakers and social scientists to design targeted interventions aimed at enhancing happiness across different population segments.
+
+This paper is structured as follows: @sec-intro introduces the context and objectives of the study.
+@sec-data outlines the dataset and describes the selection of key variables.
+@sec-model presents the Bayesian logistic regression framework employed in the analysis.
+@sec-result discusses the findings, focusing on the effects of job satisfaction, marital status, and other predictors.
+@sec-discussion explores the broader implications, limitations, and potential directions for future research, while @sec-model-details provides detailed diagnostics and validation to ensure the robustness of the results.
 
@@
 
-The estimand of this study is the probability of an individual self-reporting as "very happy." Since happiness is a subjective experience influenced by a wide range of complex factors, it is practically challenging to conduct a comprehensive survey of the happiness levels of the entire population.
-Therefore, this study utilizes sample data from the **GSS Data Explorer** and applies a Bayesian logistic regression model to estimate this probability.
+The estimand of this study is the probability of an individual self-reporting as "very happy." Since happiness is a subjective experience influenced by a wide range of complex factors, it is practically challenging to conduct a detailed survey of the happiness levels of the entire population.
+Therefore, this study utilizes sample data from the GSS Data Explorer and applies a Bayesian logistic regression model to estimate this probability.
 The sample data includes variables such as marital status, job satisfaction, income, education level, age, gender, and the number of children, representing both personal characteristics and socio-economic factors.
@@
 Through this model, the study aims to quantify the independent impact of each variable on happiness, assessing their contributions to individual happiness while controlling for other factors.
-The findings not only provide deeper insights into the determinants of happiness but also offer empirical support for policies aimed at enhancing societal well-being.
+The findings not only provide a better understanding of the determinants of happiness but also offer empirical support for policies aimed at enhancing societal well-being.
 
@@
 
-The data used in this study was sourced from the [GSS Data Explorer](https://gssdataexplorer.norc.org/MyGSS) [@gssdataexplorer], an online platform maintained by NORC that provides a wide range of resources from the General Social Survey (GSS).
-The GSS dataset includes extensive information on social, economic, and personal characteristics, making it an essential tool for studying social behaviors and trends.
-This study utilized relevant data downloaded from the platform and performed filtering and preprocessing to focus on factors influencing happiness.
+The data utilized in this study was sourced from the [GSS Data Explorer](https://gssdataexplorer.norc.org/MyGSS) [@gssdataexplorer], an online platform maintained by NORC that provides an extensive repository of information collected through the General Social Survey (GSS).
+The GSS dataset captures a wide range of social, economic, and personal characteristics, making it a useful resource for analyzing societal behaviors and trends.
+For this study, the primary focus was on variables directly related to individual happiness, such as marital status, job satisfaction, income, education, gender, age, and the number of children.
+
+In addition to the GSS dataset, there are other datasets that could have been used to analyze the factors influencing happiness.
+For example, the European Social Survey (ESS) provides rich data on life satisfaction and happiness, but it primarily focuses on European countries, making it less suitable for this study's focus on American society.
+In contrast, the GSS dataset is centered on the U.S.
+population, offering more relevant data for examining the impact of socio-economic conditions and personal characteristics on happiness in the United States.
+Similarly, the World Values Survey (WVS) offers global social-economic data, but due to its broad scope, it may not be as suitable for focusing on happiness factors specific to the U.S.
+population.
+The American Time Use Survey (ATUS) primarily focuses on time allocation rather than directly measuring life satisfaction or happiness, making it less aligned with the objectives of this study.
+The GSS dataset was chosen for its focus on U.S.
+residents and its detailed records of socio-economic and personal characteristics, which are crucial for analyzing the factors influencing happiness among Americans.
+
+The process of transforming real-world phenomena into data entries begins with the GSS survey design, where participants are asked a series of standardized questions designed to capture their demographic and socio-economic characteristics, as well as subjective well-being.
+For example:
+
+- Happiness was measured using responses to the question, *"Taking all things together, would you say you are very happy, pretty happy, or not too happy?"* Responses were coded as categorical variables in the dataset.
+
+- Income data reflects respondents' self-reported annual income, adjusted for inflation and recorded as a continuous variable.
+
+- Marital status, job satisfaction, education, and other personal attributes were captured through categorical responses, subsequently encoded into numerical or factor variables for analysis.
+
+To ensure the data's relevance to this study, preprocessing steps were undertaken.
+These included filtering the dataset to include only respondents who had complete entries for all variables of interest and standardizing continuous variables such as age and income to improve interpretability in the modeling process.
+For instance, missing data for happiness or income was excluded, and categorical variables were re-coded into binary or ordinal formats where applicable.
 
@@
 
-- **`tidyverse`** [@tidyverse]: Provided a comprehensive set of tools for data manipulation and visualization, significantly simplifying the workflow.
+- **`tidyverse`** [@tidyverse]: Provided a suite of tools for data manipulation and visualization, significantly simplifying the workflow.
 - **`palmerpenguins`** [@palmerpenguins]: Offered example datasets and tools, aiding in the quick testing of analysis code.
@@
 - **`rstanarm`** [@rstanarm]: Simplified Bayesian modeling, providing an intuitive interface for complex Bayesian analysis.
-- **`brms`** [@brms]: A flexible modeling tool built on Stan, used to perform comprehensive Bayesian regression analysis on the data.
+- **`brms`** [@brms]: A flexible modeling tool built on Stan, used to perform Bayesian regression analysis on the data.
 - **`bayesplot`**[@bayesplot]: A visualization package for Bayesian model diagnostics, posterior checks, and MCMC outputs, offering tools for clear and intuitive graphical summaries.
@@
 @tbl-happiness_preview presents the first six rows from the cleaned dataset, focusing on socio-economic and personal variables that influence happiness.
-The dataset includes key information such as marital status, job satisfaction, income, education level, age, gender, and the number of children, providing a comprehensive basis for analyzing the factors that contribute to individual happiness.
+The dataset includes key information such as marital status, job satisfaction, income, education level, age, gender, and the number of children, providing a detailed basis for analyzing the factors that contribute to individual happiness.
 
@@
 "This variable records the total number of children reported by a respondent.
-It provides insight into family size and is used to analyze its potential influence on various aspects of well-being, including happiness levels."
+It shows family size and is used to analyze its potential influence on various aspects of well-being, including happiness levels."
 
@@
 **degree:** A categorical variable indicating an individual's highest level of educational attainment (e.g., "Bachelor's").
-"This variable classifies respondents into different education categories, such as 'Less than High School,' 'High School,' 'Bachelor's,' 'associate/junior college,' and 'Graduate.' It provides insight into the respondent's educational background and is used to analyze its potential impact on various aspects of life, including happiness levels."
+"This variable classifies respondents into different education categories, such as 'Less than High School,' 'High School,' 'Bachelor's,' 'associate/junior college,' and 'Graduate.' It examines the respondent's educational background and is used to analyze its potential impact on various aspects of life, including happiness levels."
 
@@
 @fig-Degree illustrates the relationship between education level and happiness levels, with data points grouped by educational categories for clarity.
-The bars represent the proportion of happiness levels across different education levels, with distinct shades of green used to differentiate happiness categories.
-The chart highlights that individuals with higher education levels, such as graduate degrees, tend to report slightly higher levels of happiness, while other education levels show more balanced distributions.
-The use of proportional stacking and color differentiation aids in visually comparing trends across education levels.
+The bars display the proportion of happiness levels by education categories, using distinct shades of green to represent happiness levels.
+The chart indicates that individuals with higher education, such as graduate degrees, are more likely to report higher happiness levels, while other education categories exhibit more uniform distributions.
+Proportional stacking and color differentiation help compare trends effectively across education levels.
 
@@
 **satjob:** A categorical variable indicating an individual's level of job satisfaction (e.g., "Very Satisfied").
-"This variable classifies respondents into different job satisfaction categories, such as 'Very Satisfied,' 'Moderately Satisfied,' 'A Little Dissatisfied,' and 'Very Dissatisfied.' It provides insight into the respondent's feelings about their job and is used to analyze its potential impact on various aspects of well-being, including happiness levels."
+"This variable categorizes respondents by their job satisfaction levels: 'Very Satisfied,' 'Moderately Satisfied,' 'A Little Dissatisfied,' and 'Very Dissatisfied.' It indicates respondents' attitudes toward their jobs and is analyzed for its influence on happiness levels."
 
@@
 @fig-Satjob illustrates the relationship between job satisfaction and happiness levels, with data points grouped by satisfaction categories for clarity.
-The bars represent the proportion of happiness levels across different job satisfaction levels, with distinct shades of green used to differentiate happiness categories.
-The chart highlights that individuals who are more satisfied with their jobs tend to report higher levels of happiness, while those with lower satisfaction show a more diverse distribution.
-The use of proportional stacking and color differentiation helps in visually comparing the trends across job satisfaction levels.
+The bars display the proportion of happiness levels by job satisfaction categories, using distinct shades of green to represent happiness levels.
+The chart indicates that individuals with higher job satisfaction are more likely to report greater happiness, while those with lower satisfaction exhibit a broader distribution.
+Proportional stacking and color differentiation facilitate comparisons across job satisfaction levels.
 
@@
 **realrinc:** A numerical variable indicating an individual's real income (e.g., "50000").
-"This variable measures the respondent's actual income adjusted for inflation, providing a more accurate representation of purchasing power.
-It is used to classify respondents into different income levels and analyze its potential impact on various aspects of well-being, including happiness levels.
-Real income offers valuable insights into the economic conditions of respondents and their correlation with life satisfaction."
+"This variable represents respondents' inflation-adjusted income, accurately reflecting their purchasing power.
+It classifies respondents into income levels and analyzes its impact on happiness.
+Real income captures economic conditions and their association with life satisfaction."
 
@@
 
-The predictors in the model include marital status, number of children, age, education level, gender, job satisfaction, and real income.
-The Bayesian model was fitted using the `brm` function from the brms package [@brms] in R.
-The model uses a Bernoulli family with a logit link, and priors were specified as $\text{Normal}(0, 2)$ for coefficients and $\text{Cauchy}(0, 2)$ for the intercept, reflecting weakly informative prior beliefs about the effects of each predictor.
+In constructing the model, the predictors selected are directly aligned with the variables discussed in the data section.
+For example, marital status is included as it is a key socio-economic factor influencing happiness, with prior research showing its strong relationship to well-being.
+Number of children is included as it can introduce both positive and negative effects on happiness, depending on familial dynamics and financial responsibilities.
+This variable was treated as a continuous predictor, capturing the direct impact of family size, rather than categorizing it into bins, to retain the detailed effects of the number of children.
+
+Age was treated as a continuous variable, rather than categorizing it into specific age groups, in order to retain more detailed information and reflect the continuous nature of age's impact on happiness, as supported by prior literature.
+This decision avoids the loss of variability that might occur with grouped age ranges.
+Similarly, education level and job satisfaction are included as categorical predictors to capture distinct group differences while preserving important socio-economic distinctions that are likely to influence happiness.
+
+The inclusion of gender was based on its significant impact on well-being outcomes in previous research, allowing us to analyze how gender dynamics interact with other socio-economic factors.
+Real income is included as a continuous variable, as it reflects an individual's economic stability and directly correlates with happiness.
+The decision to treat income as continuous rather than categorizing it into income brackets helps retain detailed information about the effects of varying income levels on happiness, particularly since the impact of income on well-being may be non-linear.
+
+We employed a Bayesian Logistic Regression model using the `brm` function from the `brms` package [@brms] in R, which is particularly useful for fitting complex regression models with a probabilistic framework.
+The model assumes a Bernoulli family with a logit link, suitable for binary outcome variables like happiness.
+Weakly informative priors were applied to the coefficients (`Normal(0, 2)`) and intercept (`Cauchy(0, 2)`), reflecting our prior belief that the effects of each predictor are not strongly deviating from zero, providing flexibility for the model to learn from the data.
+
+In summary, the predictors were selected based on their relevance to understanding individual happiness, with each variable being included to reflect real-world influences as thoroughly as possible.
+The model’s specification, particularly the treatment of continuous vs.
+categorical variables, ensures that the relationships between predictors and happiness are captured with as much detail as the data allow.
 
@@
 
-The Bayesian Logistic Regression model was chosen for its ability to incorporate prior knowledge and quantify uncertainty in predictions, allowing for a nuanced understanding of the relationships between predictors and happiness.
+The Bayesian Logistic Regression model was chosen for its ability to incorporate prior knowledge and quantify uncertainty in predictions, allowing for a detailed understanding of the relationships between predictors and happiness.
 By using weakly informative priors, the model remains flexible while ensuring stable estimation of coefficients.
@@
 ## Model Summary
-We summarized the results of the Bayesian Logistic Regression model using the `summary` function in R, which provides detailed information about the estimated coefficients, their associated uncertainty, and credible intervals.
+
+We summarized the results of the Bayesian Logistic Regression model using the summary function in R, which provides detailed information about the estimated coefficients, their associated uncertainty, and credible intervals.
 The coefficients indicate the direction and magnitude of the relationship between predictors and the likelihood of being "very happy."
 
-Additionally, we performed posterior predictive checks using the `pp_check` function to evaluate the fit of the model.
-These checks demonstrated a reasonable agreement between the predicted and observed values, suggesting that the model effectively captures the patterns in the data.
+Additionally, we performed posterior predictive checks using the pp_check function to evaluate the fit of the model.
+These checks indicated a reasonable agreement between the predicted and observed values, suggesting that the model effectively captures the patterns in the data.
 
 The estimated coefficients revealed significant associations between happiness levels and predictors such as job satisfaction, marital status, and real income.
-For example, higher job satisfaction and income were associated with an increased likelihood of being "very happy." The credible intervals provided insights into the uncertainty of these estimates, ensuring a robust interpretation.
+For example, higher job satisfaction and income were associated with an increased likelihood of being "very happy." The credible intervals provided findings about the uncertainty of these estimates, ensuring a robust interpretation.
 
 We also calculated the average predicted probability of being "very happy" across the dataset, which highlights the overall effectiveness of the predictors in explaining variations in happiness levels.
-These results provide meaningful insights into the factors that contribute to individual happiness.
+These results provide meaningful findings about the factors that contribute to individual happiness.
 
@@
 
-As detailed in **@tbl-happiness_model_summary**, the coefficient summary provides quantitative insights into the socio-economic and demographic factors influencing individual happiness.
-For example, the estimated coefficient for **Marital Status: Married** is notably positive (Mean = 0.80), indicating that individuals who are married have a higher likelihood of reporting greater happiness compared to those in the reference category (e.g., never married).
+## Coefficient Summary {#sec-coefficient-summary}
 
-Conversely, the coefficient for **Number of Children** is slightly negative (Mean = -0.10), suggesting that having more children is associated with a marginal decrease in happiness, potentially reflecting the increased responsibilities and financial pressures that come with larger families.
-Similarly, the negative coefficient for **Age** (Mean = -0.02) suggests a modest decline in happiness with age.
+As detailed in @tbl-happiness_model_summary, the coefficient summary offers a quantitative perspective on the socio-economic and demographic determinants of individual happiness.
+For instance, the estimated coefficient for **Marital Status: Married** is significantly positive (Mean = 0.80), indicating that married individuals are more likely to report higher levels of happiness compared to those in the reference category (e.g., never married).
+This highlights the role of marital status in fostering emotional and social well-being.
 
-Positive coefficients for **Education Level: Graduate** (Mean = 0.50) and **Job Satisfaction: Moderately Satisfied** (Mean = 0.70) highlight the strong association between higher education, job satisfaction, and increased happiness.
-Additionally, **Real Income** (Mean = 0.02) shows a small but positive effect, indicating that higher income is correlated with greater happiness, albeit at a modest rate.
+In contrast, the coefficient for **Number of Children** is slightly negative (Mean = -0.10), suggesting that larger family sizes are associated with a marginal decrease in happiness.
+This result likely reflects the added responsibilities and financial burdens inherent in raising children.
+Similarly, the coefficient for **Age** (Mean = -0.02) suggests a gradual decline in happiness as individuals age, potentially indicating shifting priorities or life circumstances.
 
-Finally, the Intercept (Mean = -1.50) establishes the baseline log-odds for happiness, setting the reference point for interpreting the influence of these predictors.
-Together, these coefficients illuminate the multifaceted factors shaping happiness, underscoring the importance of socio-economic stability and personal well-being.
+Positive coefficients for **Education Level: Graduate** (Mean = 0.50) and **Job Satisfaction: Moderately Satisfied** (Mean = 0.70) highlight the strong relationship between higher educational attainment, workplace satisfaction, and enhanced happiness.
+Furthermore, the coefficient for **Real Income** (Mean = 0.02) demonstrates a small but positive effect, affirming the correlation between financial stability and happiness, albeit with diminishing returns.
+
+The Intercept (Mean = -1.50) serves as the baseline log-odds for happiness, providing a reference point against which the impact of other predictors is measured.
+Collectively, these coefficients clarify the complex interplay of socio-economic and demographic factors in shaping happiness, emphasizing the important role of both external stability and personal well-being in determining life satisfaction.
 
@@
 ```
-As shown in @fig-happiness_model_coefficients, the Bayesian logistic regression model visualizes the impact of predictor variables on happiness.
-Each point represents the posterior mean estimate, and the horizontal lines indicate the 90% credible intervals.
+As illustrated in @fig-happiness_model_coefficients, the Bayesian logistic regression model provides a clear visualization of the influence of predictor variables on happiness.
+Each point represents the posterior mean estimate, with horizontal lines denoting the 90% credible intervals, offering a reliable measure of uncertainty.
 Key findings include:
 
-- The variable **`Marital Status: Married`** shows a positive coefficient, indicating that married individuals report significantly higher happiness compared to the reference group (e.g., never married).
-- **`Education Level: Graduate`** and **`Job Satisfaction: Moderately Satisfied`** exhibit strong positive effects, highlighting the importance of higher education and job satisfaction in boosting happiness.
-- Conversely, **`Number of Children`** and **`Age`** show negative coefficients, suggesting that an increase in the number of children and aging slightly reduce happiness levels.
-- **`Real Income`** displays a modest positive effect, indicating that higher income is associated with increased happiness, although the effect is relatively small.
+- The coefficient for **`Marital Status: Married`** is notably positive, indicating that married individuals are significantly more likely to report higher happiness levels compared to those in the reference category (e.g., never married).
+This finding highlights the importance of marital relationships in fostering well-being.
 
-These findings provide detailed insights into the socio-economic and demographic factors influencing individual happiness.
+- **`Education Level: Graduate`** and **`Job Satisfaction: Moderately Satisfied`** exhibit substantial positive effects, underscoring the significant influence of advanced education and workplace satisfaction in enhancing happiness.
+
+- In contrast, the coefficients for **`Number of Children`** and **`Age`** are negative, suggesting that having more children and aging are associated with slight reductions in happiness.
+These results may reflect the increased financial and caregiving responsibilities tied to larger families, as well as potential shifts in life priorities with age.
+
+- The variable **`Real Income`** demonstrates a modest positive effect, signifying that higher income contributes to increased happiness, albeit with a relatively small magnitude.
+
+Taken together, these findings shed light on the complex interplay of socio-economic and demographic factors shaping individual happiness, providing strong support for targeted interventions aimed at enhancing well-being.
 
@@
 
-This paper explores the factors influencing individual happiness using a Bayesian logistic regression model to analyze self-reported happiness levels.
-By leveraging a carefully selected subset of socio-economic and demographic variables from a comprehensive dataset, this study identifies patterns that highlight key determinants of happiness and their relative importance in shaping well-being outcomes.
+This study investigates the determinants of individual happiness by employing a Bayesian logistic regression model to analyze self-reported happiness levels.
+Through the careful selection of socio-economic and demographic variables, this research identifies key factors influencing well-being and their relative importance, providing a detailed understanding of the variables shaping happiness.
 
@@
 
-This study carefully selects key variables—marital status, job satisfaction, education level, real income, age, and number of children—based on their strong association with individual happiness.
-The selection process was guided by both theoretical significance and empirical evidence, ensuring the model accurately reflects real-world influences on well-being.
-The quantitative analysis demonstrates how these variables play a pivotal role in shaping personal happiness.
-For instance, marital status and job satisfaction emerge as strong predictors, with married individuals and those who are highly satisfied with their jobs reporting significantly higher levels of happiness.
+The analysis prioritizes variables—marital status, job satisfaction, education level, income, age, and number of children—based on their theoretical relevance and empirical association with happiness.
+This selection ensures that the model reflects real-world dynamics affecting well-being.
+Findings underscore the strong predictive power of marital status and job satisfaction, as married individuals and those who report high job satisfaction are significantly more likely to describe themselves as "very happy." These results align with established theories emphasizing the role of emotional and economic stability in fostering happiness.
 
-Interestingly, the analysis reveals a nuanced relationship between the number of children and happiness.
-While having children can bring joy, larger family sizes are often associated with slightly lower levels of happiness, possibly due to increased financial and caregiving responsibilities.
-Similarly, higher levels of education and income are positively associated with happiness, illustrating the role of socio-economic stability in improving life satisfaction.
-These findings not only align with established theories but also provide a deeper understanding of the complex interactions among social, economic, and demographic factors that drive individual well-being.
+A complex relationship emerges for the number of children, where larger family sizes are associated with marginally lower happiness levels, likely due to increased caregiving and financial responsibilities.
+Similarly, age shows a slight negative association with happiness, reflecting shifts in life priorities over time.
+In contrast, higher education levels and income exhibit positive effects, reinforcing the importance of socio-economic stability and opportunities in improving life satisfaction.
+These findings provide a comprehensive perspective on the relationships among socio-economic and demographic factors influencing happiness.
 
@@
 
-By selecting variables with strong associations to individual happiness—such as marital status, job satisfaction, education level, income, age, and number of children—this study underscores the multifaceted nature of well-being.
-The inclusion of these variables reflects both theoretical relevance and empirical robustness, providing insights into the dynamics of happiness.
-For example, focusing on the positive impact of marriage and job satisfaction aligns with broader sociological findings about emotional and economic stability.
+The deliberate focus on variables with strong theoretical and empirical foundations underscores the diverse factors contributing to happiness.
+Marital status and job satisfaction emerge as robust predictors, reflecting their significant emotional and economic impact.
+The inclusion of education and income highlights the role of socio-economic stability in fostering well-being, while the effects of age and family size reveal deeper complexities in how life circumstances shape happiness.
 
-Interestingly, while other variables, such as detailed occupational categories or regional distinctions, were excluded to streamline the analysis, their potential impact opens avenues for future research.
-Future investigations could explore how specific professions or geographic contexts influence happiness, shedding light on how cultural and environmental factors interact with socio-economic predictors.
-This targeted approach not only refines current models but also lays the groundwork for exploring the broader complexities of what drives individual happiness.
+Although this study excludes variables such as occupational categories or regional differences to streamline the model, these factors represent promising avenues for future research.
+For example, exploring the influence of specific professions or geographic contexts could reveal cultural and environmental interactions with socio-economic predictors.
+Such investigations would refine current models and expand the understanding of happiness determinants.
 
@@
 
-While this study provides valuable insights into the factors influencing individual happiness, its scope is limited by the variables included and the dataset size.
-The exclusion of variables such as region of residence or specific occupational categories, though aimed at simplifying the model, restricts the depth of analysis.
-Future research could incorporate these variables to better understand the interplay of geographical, cultural, and professional contexts on happiness.
+Despite its contributions, this study is limited by the scope of variables included and the dataset's size.
+Excluding variables such as region or health conditions narrows the analysis and leaves room for future research to provide a more holistic perspective.
+Incorporating additional dimensions, such as leisure activities or access to healthcare, could further enhance the model's explanatory power.
 
-Moreover, the model could be enhanced by exploring additional dimensions, such as health conditions or leisure time, to provide a more holistic view of well-being.
-Integrating data from broader samples across different regions or including longitudinal datasets could improve the model’s generalizability and offer insights into how happiness evolves over time.
+Expanding the dataset to include broader samples across diverse regions or employing longitudinal data could improve generalizability and offer insights into how happiness evolves over time.
+Moreover, investigating the impact of external socio-economic factors, such as public policy changes or economic crises, could reveal macro-level influences on well-being.
 
-Another avenue for future exploration involves examining the impact of external socio-economic factors, such as economic downturns or public policy changes, on happiness.
-For example, understanding how financial crises or access to social services influence happiness levels could inform policies aimed at improving societal well-being.
+Advancements in analytical methods, such as machine learning techniques, could uncover complex, non-linear relationships among variables that traditional regression models may overlook.
+For instance, examining interactions between age, income, and job satisfaction could illuminate critical periods and conditions for optimal well-being.
 
-Additionally, the use of advanced machine learning techniques could help uncover hidden patterns and interactions among variables that traditional regression models might miss.
-For instance, exploring non-linear relationships between age, income, and happiness could yield deeper insights into the life stages most conducive to well-being.
-
-These research directions not only build upon the findings of this study but also provide opportunities to address its limitations, contributing to a more comprehensive understanding of the determinants of happiness in diverse contexts.
+These directions not only address the limitations of this study but also pave the way for a more comprehensive understanding of happiness in varied contexts, advancing both academic and policy-oriented research.
 
@@
 
-The potential for future research based on this dataset is vast.
-One promising avenue involves investigating the intersection between happiness and broader societal factors, such as access to healthcare or the availability of social support systems.
-By integrating external datasets, future studies could explore how these contextual elements amplify or mitigate the effects of individual-level predictors like income or job satisfaction.
+The dataset’s rich potential invites exploration of broader societal influences on happiness.
+For instance, integrating external datasets to examine the role of social support systems, healthcare access, or environmental quality could illuminate contextual factors that amplify or mitigate individual-level predictors.
 
-Another intriguing possibility is examining how happiness evolves across different life stages, using longitudinal data to track changes over time.
-Such research could illuminate critical periods where interventions might have the greatest impact on well-being.
+Longitudinal analyses offer another promising direction, enabling researchers to track changes in happiness over time and identify key life stages for intervention.
+Similarly, incorporating geographical data could uncover regional variations in happiness, allowing for nuanced analyses of cultural and environmental determinants.
 
-Additionally, incorporating geographical data could provide a deeper understanding of regional variations in happiness, allowing for an analysis of how cultural or environmental factors shape well-being.
-The dataset’s richness opens the door to these and many other avenues for advancing our understanding of the complex drivers of happiness.
+By building on this study’s findings, future research can deepen our understanding of happiness drivers, enhancing both theoretical frameworks and practical applications aimed at improving well-being.
 
@@
 
-This research highlights the analytical value of understanding the factors that drive individual happiness, such as the significant role of marital status and job satisfaction.
-These findings can inform policy development and workplace strategies aimed at improving well-being.
-The positive correlation between higher education levels and happiness also emphasizes the broader societal value of investing in accessible and equitable education systems, reflecting the importance of socio-economic stability in fostering life satisfaction.
+This study demonstrates the importance of understanding the determinants of happiness.
+Findings such as the significant roles of marital status and job satisfaction offer actionable recommendations for policymakers and employers to design strategies aimed at enhancing well-being.
+The positive relationship between higher education and happiness emphasizes the societal importance of investing in equitable education systems, reinforcing the role of socio-economic stability in fostering life satisfaction.
+
+By advancing the understanding of happiness drivers, this research contributes to the broader discourse on well-being and offers a foundation for future studies and interventions aimed at improving individual and societal outcomes.
 
@@
 This plot compares the observed data (*y*) with the replicated data (*y_rep*) generated by the model.
-The overlaid density curves represent multiple posterior predictive distributions, visually demonstrating how well the model captures the observed data.
-The close alignment of the observed and predicted distributions suggests that the model provides a reasonable fit, effectively capturing both the central tendencies and variability in the data.
+The overlaid density curves represent multiple posterior predictive distributions, visually indicating how well the model aligns with the observed data.
+The close alignment of the observed and predicted distributions suggests that the model provides a reasonable fit, accurately reflecting both central tendencies and variability in the data.
 
 In @fig-ppcheckandposteriorvsprior-2, we compare the posterior distributions of the model parameters with their corresponding priors.
-This plot illustrates the extent to which the data influences the parameter estimates.
-The divergence between the posterior and prior distributions reflects the strength of the evidence provided by the data, demonstrating how the Bayesian model updates prior assumptions to produce refined parameter estimates.
-This comparison underscores the importance of data in shaping the final inference and validating the robustness of the model.
+This plot illustrates the influence of the data on parameter estimates.
+The divergence between the posterior and prior distributions highlights the strength of the evidence provided by the data, showing how the Bayesian model refines prior assumptions to produce updated parameter estimates.
+This comparison emphasizes the role of the data in shaping final inferences and validating the robustness of the model.
 
@@
 @fig-stanareyouokay-1 is a trace plot, depicting the sampled values of each parameter over iterations.
-The plot shows that the chains for each parameter exhibit patterns resembling a 'hairy caterpillar,' indicating well-mixed chains that thoroughly explore the posterior distribution.
-This visual evidence strongly suggests that the Markov chains have likely converged, ensuring the reliability of posterior estimates.
+The plot shows that the chains for each parameter exhibit patterns resembling a 'hairy caterpillar,' indicating well-mixed chains that effectively explore the posterior distribution.
+This evidence suggests that the Markov chains have likely converged, ensuring the reliability of posterior estimates.
 
-This plot is a crucial diagnostic tool, verifying that the sampling process is effective and that the model's posterior distributions are credible.
+This plot serves as a key diagnostic tool, verifying that the sampling process is efficient and that the model's posterior distributions are credible.
 
-As shown in @fig-stanareyouokay-2, the Rhat values are close to 1, indicating that the chains have likely converged and the model results are reliable.
+As shown in @fig-stanareyouokay-2, the Rhat values are close to 1, further confirming that the chains have likely converged and the model results are reliable.
 
-Together, these diagnostic plots affirm the validity of the Bayesian model's posterior distributions, enabling trustworthy inference based on the sampled data.
+Together, these diagnostic plots validate the Bayesian model's posterior distributions, supporting robust inference based on the sampled data.
 
@@
 Each horizontal line represents the **90% credible interval**, centered around the median of the posterior distribution for a given parameter.
-The shaded areas depict the density of the posterior distribution, providing insights into the uncertainty and variability of the parameter estimates.
+The shaded areas depict the density of the posterior distribution, illustrating the uncertainty and variability of the parameter estimates.
 
 The parameters encompass socio-economic and demographic factors, such as marital status, job satisfaction, education level, and income.
-Notably, parameters like **Marital Status: Married** and **Job Satisfaction: Very Satisfied** exhibit positive median values, suggesting a strong positive association with happiness.
-In contrast, variables such as **Number of Children** and **Age** show slightly negative median values, indicating a modest decline in happiness with increasing age and family size.
-This visualization highlights the nuanced relationships between these predictors and individual happiness.
+Notably, parameters like **Marital Status: Married** and **Job Satisfaction: Very Satisfied** exhibit positive median values, indicating a positive association with happiness.
+In contrast, variables such as **Number of Children** and **Age** show slightly negative median values, reflecting a modest decline in happiness with increasing age and family size.
+This visualization emphasizes the complex relationships between these predictors and individual happiness.
 
@@
 
+Welcome to the "Factors Influencing Happiness Survey." This survey seeks to explore the relationship between socio-economic factors, personal characteristics, and individual well-being.
+Your responses will remain anonymous and contribute to research aimed at understanding the determinants of happiness.
+Completing the survey will take approximately 5–7 minutes.
+Thank you for your valuable participation!
+
+If you have any questions or concerns, please contact:
+
+- **Survey Coordinator**: Shuheng (Jack) Zhou
+- **Email**: [shuheng.zhou@mail.utoronto.ca](mailto:shuheng.zhou@mail.utoronto.ca)
+
 1. **What is your marital status?**

### 2024-12-03 paper/paper.qmd
make some changes

@@
 # Data {#sec-data}
-
-## Measurement
+## Data Source
 
@@
 residents and its detailed records of socio-economic and personal characteristics, which are crucial for analyzing the factors influencing happiness among Americans.
+
+## Measurement
 
@@
 #| label: tbl-happiness_preview
-#| tbl-cap: "Happiness Data Sample Preview"
+#| tbl-cap: "Sample Preview of Happiness Data: A snapshot showing key variables"
 
@@
 
-## variables
+## Variables
 
@@
 #| warning: false
-#| label: fig-Marital
-#| fig-cap: Happiness Levels Across Different Marital Statuses
+#| label: fig-MaritalStatusDistribution
+#| fig-cap: "Happiness Levels Across Different Marital Statuses: Depicting the Distribution of Self-Reported Happiness Levels ('Very Happy', 'Pretty Happy', 'Not Too Happy') by Marital Status Categories"
 
@@
 
-@fig-Marital illustrates the relationship between marital status and happiness levels, with data points grouped by marital categories for clarity.
+@fig-MaritalStatusDistribution illustrates the relationship between marital status and happiness levels, with data points grouped by marital categories for clarity.
 The bars represent the distribution of happiness levels across different marital statuses, with distinct shades of green used to differentiate happiness levels.
@@
 #| warning: false
-#| label: fig-Childs
-#| fig-cap: Distribution of the Number of Children by Happiness Level
+#| label: fig-ChildrenDistribution
+#| fig-cap: "Distribution of the Number of Children by Happiness Level: Showing Family Size Across Different Happiness Categories"
 
@@
 
-# Create a boxplot
+# Create a violin plot with jittered points
 ggplot(data, aes(x = happy, y = childs, fill = happy)) +
-  geom_boxplot(outlier.color = "red", outlier.size = 1.5) +  # Show outliers as red dots
+  geom_violin(trim = TRUE, alpha = 0.7) +  # Violin plot to show distribution
+  geom_jitter(width = 0.2, alpha = 0.4, color = "black", size = 1) +  # Add jitter points for raw data
   scale_fill_manual(values = c(
@@
     axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
-    plot.title = element_text(face = "bold", hjust = 0.5)  # Bold and center the title
+    plot.title = element_text(face = "bold", hjust = 0.5),  # Bold and center the title
+    legend.title = element_text(face = "bold"),  # Bold legend title
+    panel.grid.major = element_blank(),  # Remove major gridlines
+    panel.grid.minor = element_blank()   # Remove minor gridlines
   )
@@
 ```
-@fig-Childs illustrates the relationship between the number of children and happiness levels, with data points grouped by happiness categories for clarity.
-The boxplots represent the distribution of the number of children across different happiness levels, using distinct shades of green to differentiate happiness categories.
-The chart highlights that the distribution of the number of children is relatively similar across happiness levels, with a few outliers indicating families with a higher number of children.
-The use of color and boxplot structure aids in visually comparing the distributions between categories.
+@fig-ChildrenDistribution illustrates the relationship between the number of children and happiness levels, with data points grouped by happiness categories for better clarity.
+The violin plots display the density distribution of the number of children across the three happiness levels: "Not Too Happy," "Pretty Happy," and "Very Happy," differentiated by distinct shades of green.
+Additionally, jittered points overlay the violin plots, representing individual observations, thereby providing a detailed view of the raw data.
+
+The chart highlights that the number of children is distributed similarly across happiness levels, with the highest density of observations clustering around smaller family sizes.
+A few data points stand out as outliers, representing families with larger numbers of children.
+This combination of violin plots and jittered points effectively showcases both the overall trends and individual variances, making the relationships between family size and happiness levels visually accessible and easy to interpret.
 
@@
 #| warning: false
-#| label: fig-Degree
-#| fig-cap: Proportion of Happiness Levels by Education Level
+#| label: fig-EducationHappinessDistribution
+#| fig-cap: "Proportion of Happiness Levels by Education Level: Representing the Distribution of Happiness Categories Across Different Levels of Educational Attainment"
 
@@
 ```
-@fig-Degree illustrates the relationship between education level and happiness levels, with data points grouped by educational categories for clarity.
+@fig-EducationHappinessDistribution illustrates the relationship between education level and happiness levels, with data points grouped by educational categories for clarity.
 The bars display the proportion of happiness levels by education categories, using distinct shades of green to represent happiness levels.
@@
 #| warning: false
-#| label: fig-Satjob
-#| fig-cap: Proportion of Happiness Levels by Job Satisfaction
+#| label: fig-JobSatisfactionHappiness
+#| fig-cap: "Proportion of Happiness Levels by Job Satisfaction: Depicting the Distribution of Self-Reported Happiness Categories Across Different Job Satisfaction Levels"
 
@@
 ```
-@fig-Satjob illustrates the relationship between job satisfaction and happiness levels, with data points grouped by satisfaction categories for clarity.
+@fig-JobSatisfactionHappiness illustrates the relationship between job satisfaction and happiness levels, with data points grouped by satisfaction categories for clarity.
 The bars display the proportion of happiness levels by job satisfaction categories, using distinct shades of green to represent happiness levels.
@@
 #| warning: false
-#| label: fig-Realrinc
-#| fig-cap: Real Income vs. Happiness Level
+#| label: fig-IncomeHappiness
+#| fig-cap: "Real Income and Happiness Level: This analysis explores the distribution of real income across different happiness categories, using jitter points to illustrate the variability of individual data within each category"
 
@@
 ```
-@fig-Realrinc illustrates the relationship between real income and happiness levels, with data points grouped by happiness categories for clarity.
+@fig-IncomeHappiness illustrates the relationship between real income and happiness levels, with data points grouped by happiness categories for clarity.
 The scatter plot shows the distribution of real income across different happiness levels, using distinct shades of green to differentiate happiness categories.
@@
 These results provide meaningful findings about the factors that contribute to individual happiness.
+
+## Model Limitations
+
+Although the Bayesian logistic regression model performs well in analyzing the relationship between happiness and its predictors, it still has certain limitations.
+First, the model assumes a linear relationship between the predictors and the log-odds of happiness, which may overlook complex non-linear or interaction effects between variables.
+For example, the relationship between age and happiness may exhibit non-linear patterns, leading to potential biases in estimation.
+Second, the imbalanced distribution of categories in the data—where the "very happy" category has fewer samples—may cause the model to favor predicting the majority classes (e.g., "not too happy" and "pretty happy") while underperforming in classifying the minority class.
+Lastly, the model employs weakly informative priors (e.g., Normal(0, 2) and Cauchy(0, 2)) to ensure flexibility.
+However, in cases with small samples or rare categories, these priors may impact the stability of coefficient estimates, increasing uncertainty in the results.
+
+## Alternative Models Considered
+
+The Bayesian logistic regression model was chosen due to its unique ability to incorporate prior knowledge, quantify uncertainty, and provide robust parameter estimates in the analysis of complex individual-level happiness data.
+Unlike traditional logistic regression, the Bayesian framework allows for the inclusion of weakly informative priors, which help stabilize estimates in the presence of limited or imbalanced data (e.g., the "very happy" category being underrepresented) while avoiding overfitting.
+This is particularly advantageous in handling imbalanced target variable distributions, where the Bayesian model performs better in classifying minority categories.
+Additionally, the Bayesian model computes posterior distributions for each predictor, offering a comprehensive understanding of the uncertainty and variability in the estimated effects.
+This probabilistic framework not only enhances interpretability but also supports better decision-making by providing credible intervals instead of single-point estimates.
+
+In contrast, other models such as decision trees may perform poorly when analyzing complex social data.
+While decision trees offer advantages in interpretability and handling non-linear relationships, they are highly sensitive to changes in data distribution and noise.
+In cases of class imbalance, decision trees tend to overfit the majority class, reducing their predictive accuracy for underrepresented categories.
+Moreover, decision trees lack the ability to provide posterior distributions or quantify uncertainty, making it challenging to robustly evaluate the effects of predictors.
+These limitations render decision trees less reliable for analyzing complex problems like happiness data.
+
+For these reasons, the Bayesian logistic regression model stands out for its flexibility and robustness, capturing complex non-linear relationships and potential interactions while quantifying uncertainty.
+It offers more accurate and comprehensive insights for predicting happiness compared to alternative models, making it a superior choice for this analysis.
 
@@
 # Appendix {-}
+
+# Data cleaning process
+
+To prepare the dataset for analysis, I conducted a thorough cleaning process to address missing values, inconsistent formatting, and invalid entries, ensuring the data’s accuracy and usability.
+The cleaning steps were designed to align with the study’s focus on socio-economic and personal factors influencing happiness.
+
+## Handling Missing and Invalid Values
+
+- In the `realrinc` (real income) column, entries coded as `-100` were replaced with `NA` to signify missing data, as `-100` was an invalid placeholder value.
+
+- For categorical variables like `marital`, `degree`, `satjob`, and `happy`, entries such as `.n: no answer` and `.d: do not know/cannot choose` were converted to `NA` to exclude non-informative responses.
+Additionally, in the `satjob` column, responses marked as `.i: inapplicable` were also replaced with `NA` to ensure only relevant data remained.
+
+## Standardizing Categorical Data
+
+- Categorical variables, including `marital`, `degree`, `sex`, `happy`, `satjob`, and `ballot`, were cleaned by removing extra spaces and converting all text to lowercase to maintain consistency and facilitate accurate analysis.
+
+## Adjusting the `childs` Column
+
+- Entries labeled as `"8 or more"` in the `childs` (number of children) column were replaced with `8`, as this was the maximum numeric representation available.
+This transformation allowed the variable to be converted into a numeric format for quantitative analysis.
+
+## Converting Data Types
+- Variables like `age` and `childs` were converted to numeric data types to enable proper statistical analysis and modeling.
+
+## Filtering Irrelevant Responses
+- Rows where the `happy` variable contained responses like `.d: do not know/cannot choose` or `.n: no answer` were removed to ensure the dataset only included valid observations relevant to the study’s goal of understanding happiness.
+
+## Summary
+These cleaning steps were essential for maintaining data integrity and ensuring that the analysis would provide meaningful and reliable results.
+By standardizing and filtering the data, the study could focus on valid and interpretable responses, minimizing noise and maximizing the quality of insights derived from the dataset.
 

### 2024-12-03 scripts/06-model_data.R

@@ -9,15 +9,10 @@
 
 
 # Install and load necessary packages
-if (!requireNamespace("brms", quietly = TRUE)) {
-  install.packages("brms")
-}
-if (!requireNamespace("arrow", quietly = TRUE)) {
-  install.packages("arrow")
-}
 library(dplyr)
 library(brms)
 library(arrow)
+library(rstanarm)
 
 # Load data
 data <- read_parquet("data/02-analysis_data/cleaned_happiness_data.parquet")

### 2024-12-03 paper/paper.qmd
make some changes

@@
 [@helliwell2020] have highlighted the importance of social connections and subjective well-being, suggesting that these dimensions often outweigh purely economic metrics.
-Despite these valuable contributions, a notable issue persists in understanding how socio-economic factors interact with personal characteristics—such as marital status, gender, and the number of children—in shaping happiness.
+Despite these meaningful contributions, a notable issue persists in understanding how socio-economic factors interact with personal characteristics—such as marital status, gender, and the number of children—in shaping happiness.
 
@@
 
-These results validate earlier findings on the importance of socio-economic stability while offering new insights into how demographic factors influence well-being.
+These results validate earlier findings on the importance of socio-economic stability while offering new findings into how demographic factors influence well-being.
 The study provides practical recommendations for policymakers and social scientists to design targeted interventions aimed at enhancing happiness across different population segments.
@@
 The GSS dataset was chosen for its focus on U.S.
-residents and its detailed records of socio-economic and personal characteristics, which are crucial for analyzing the factors influencing happiness among Americans.
+residents and its detailed records of socio-economic and personal characteristics, which are essential for analyzing the factors influencing happiness among Americans.
 
@@
 - **`bayesplot`**[@bayesplot]: A visualization package for Bayesian model diagnostics, posterior checks, and MCMC outputs, offering tools for clear and intuitive graphical summaries.
+- **`testthat`** [@testthat]: Enabled modular and reproducible testing of data and analysis workflows, ensuring the validity of datasets, functions, and model outputs while enhancing code reliability.
 
@@
 
-**`age`**: Represents the respondent's age, measured in years.
-
-**`sex`**: Denotes the biological sex of the respondent, categorized as: **male** and **female**.
+**age**: Represents the respondent's age, measured in years.
+
+**sex**: Denotes the biological sex of the respondent, categorized as: male and female.
+
+**childs:** A numerical variable indicating the number of children an individual has (e.g., 2).
+"This variable records the total number of children reported by a respondent.
+It shows family size and is used to analyze its potential influence on various aspects of well-being, including happiness levels."
 
 **marital:** A categorical variable indicating an individual's marital status (e.g., "Married").
-"This variable classifies respondents into different marital categories, such as 'Married,' 'Never Married,' 'Divorced,' 'Widowed,' or 'Separated.' It provides insight into the respondent's current relationship status and is used to analyze its potential impact on various factors, including happiness levels."
+"This variable classifies respondents into different marital categories, such as 'Married,' 'Never Married,' 'Divorced,' 'Widowed,' or 'Separated.' It provides finding into the respondent's current relationship status and is used to analyze its potential impact on various factors, including happiness levels."
 
@@
 
-**childs:** A numerical variable indicating the number of children an individual has (e.g., 2).
-"This variable records the total number of children reported by a respondent.
-It shows family size and is used to analyze its potential influence on various aspects of well-being, including happiness levels."
-
-```{r}
-#| echo: false
-#| warning: false
-#| label: fig-ChildrenDistribution
-#| fig-cap: "Distribution of the Number of Children by Happiness Level: Showing Family Size Across Different Happiness Categories"
-
-# Filter out non-finite values (NA or Inf)
-data <- data %>%
-  filter(!is.na(childs), is.finite(childs))  # Remove NA or infinite values
-
-# Create a violin plot with jittered points
-ggplot(data, aes(x = happy, y = childs, fill = happy)) +
-  geom_violin(trim = TRUE, alpha = 0.7) +  # Violin plot to show distribution
-  geom_jitter(width = 0.2, alpha = 0.4, color = "black", size = 1) +  # Add jitter points for raw data
-  scale_fill_manual(values = c(
-    "pretty happy" = "#41AB5D",  # Dark green
-    "very happy" = "#00441B",    # Medium green
-    "not too happy" = "#A1D99B"  # Light green
-  )) +
-  theme_minimal() +
-  labs(
-    x = "Happiness Level",
-    y = "Number of Children",
-    fill = "Happiness Level"
-  ) +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
-    plot.title = element_text(face = "bold", hjust = 0.5),  # Bold and center the title
-    legend.title = element_text(face = "bold"),  # Bold legend title
-    panel.grid.major = element_blank(),  # Remove major gridlines
-    panel.grid.minor = element_blank()   # Remove minor gridlines
-  )
-
-```
-@fig-ChildrenDistribution illustrates the relationship between the number of children and happiness levels, with data points grouped by happiness categories for better clarity.
-The violin plots display the density distribution of the number of children across the three happiness levels: "Not Too Happy," "Pretty Happy," and "Very Happy," differentiated by distinct shades of green.
-Additionally, jittered points overlay the violin plots, representing individual observations, thereby providing a detailed view of the raw data.
-
-The chart highlights that the number of children is distributed similarly across happiness levels, with the highest density of observations clustering around smaller family sizes.
-A few data points stand out as outliers, representing families with larger numbers of children.
-This combination of violin plots and jittered points effectively showcases both the overall trends and individual variances, making the relationships between family size and happiness levels visually accessible and easy to interpret.
-
-\newpage
-
 **degree:** A categorical variable indicating an individual's highest level of educational attainment (e.g., "Bachelor's").
@@
 
-Education level (degree) provides insight into the role of knowledge and opportunity in shaping well-being, while age captures generational and life-stage effects that may influence happiness levels.
+Education level (degree) provides finding into the role of knowledge and opportunity in shaping well-being, while age captures generational and life-stage effects that may influence happiness levels.
 The inclusion of gender (sex) enables us to investigate potential disparities in reported happiness between men and women.
@@
 By using weakly informative priors, the model remains flexible while ensuring stable estimation of coefficients.
-This approach is particularly valuable for exploring individual-level happiness data, where complex interactions and varying effects are expected across predictors.
+This approach is particularly meaningful for exploring individual-level happiness data, where complex interactions and varying effects are expected across predictors.
 
@@
 
-The estimated coefficients revealed significant associations between happiness levels and predictors such as job satisfaction, marital status, and real income.
+The estimated coefficients indicated significant associations between happiness levels and predictors such as job satisfaction, marital status, and real income.
 For example, higher job satisfaction and income were associated with an increased likelihood of being "very happy." The credible intervals provided findings about the uncertainty of these estimates, ensuring a robust interpretation.
@@
 
-## Model Limitations
-
-Although the Bayesian logistic regression model performs well in analyzing the relationship between happiness and its predictors, it still has certain limitations.
-First, the model assumes a linear relationship between the predictors and the log-odds of happiness, which may overlook complex non-linear or interaction effects between variables.
-For example, the relationship between age and happiness may exhibit non-linear patterns, leading to potential biases in estimation.
-Second, the imbalanced distribution of categories in the data—where the "very happy" category has fewer samples—may cause the model to favor predicting the majority classes (e.g., "not too happy" and "pretty happy") while underperforming in classifying the minority class.
-Lastly, the model employs weakly informative priors (e.g., Normal(0, 2) and Cauchy(0, 2)) to ensure flexibility.
-However, in cases with small samples or rare categories, these priors may impact the stability of coefficient estimates, increasing uncertainty in the results.
+## Model Assumptions and Limitations
+
+The Bayesian logistic regression model is built upon several key assumptions that underpin its structure and interpretation.
+First, the model assumes a linear relationship between the predictors and the log-odds of happiness, meaning that the effects of predictors remain constant across their range.
+This assumption simplifies the modeling process but may fail to capture complex non-linear patterns or interactions between variables, such as potential non-linear relationships between age and happiness.
+The model also assumes independence between predictors, which may not hold in real-world data where multicollinearity or interaction effects are common.
+Additionally, the model relies on weakly informative priors (e.g., Normal(0, 2) for coefficients and Cauchy(0, 2) for the intercept) to provide flexibility while avoiding overfitting.
+While these priors stabilize the estimation process, they may still introduce bias or increase uncertainty in cases with small samples or sparse categories.
+Lastly, the model assumes homoscedasticity and Gaussian-distributed residuals, which may not fully account for variability or skewness in happiness data.
+
+Despite its strengths, the model has certain limitations that should be noted.
+First, the linearity assumption between predictors and log-odds may oversimplify relationships, leading to potential biases in effect estimation.
+For instance, the relationship between income and happiness might exhibit diminishing returns, which a linear model may struggle to capture.
+Second, the imbalanced distribution of the target variable—where "very happy" is a minority category—presents a challenge, as the model may prioritize predicting majority categories ("not too happy" and "pretty happy") while underperforming in classifying the minority category.
+Additionally, while weakly informative priors are generally robust, they may lead to unstable coefficient estimates in cases of sparse data or rare categories, increasing uncertainty in the results.
+The assumption of homoscedasticity may also be violated in situations where variability in happiness levels depends on specific predictors, such as income or job satisfaction.
 
@@
 This is particularly advantageous in handling imbalanced target variable distributions, where the Bayesian model performs better in classifying minority categories.
-Additionally, the Bayesian model computes posterior distributions for each predictor, offering a comprehensive understanding of the uncertainty and variability in the estimated effects.
+Additionally, the Bayesian model computes posterior distributions for each predictor, offering a detailed understanding of the uncertainty and variability in the estimated effects.
 This probabilistic framework not only enhances interpretability but also supports better decision-making by providing credible intervals instead of single-point estimates.
@@
 For these reasons, the Bayesian logistic regression model stands out for its flexibility and robustness, capturing complex non-linear relationships and potential interactions while quantifying uncertainty.
-It offers more accurate and comprehensive insights for predicting happiness compared to alternative models, making it a superior choice for this analysis.
+It offers more accurate and detailed findings for predicting happiness compared to alternative models, making it a superior choice for this analysis.
 
@@
 In contrast, higher education levels and income exhibit positive effects, reinforcing the importance of socio-economic stability and opportunities in improving life satisfaction.
-These findings provide a comprehensive perspective on the relationships among socio-economic and demographic factors influencing happiness.
+These findings provide a detailed perspective on the relationships among socio-economic and demographic factors influencing happiness.
 
@@
 Marital status and job satisfaction emerge as robust predictors, reflecting their significant emotional and economic impact.
-The inclusion of education and income highlights the role of socio-economic stability in fostering well-being, while the effects of age and family size reveal deeper complexities in how life circumstances shape happiness.
+The inclusion of education and income highlights the role of socio-economic stability in fostering well-being, while the effects of age and family size indicate deeper complexities in how life circumstances shape happiness.
 
 Although this study excludes variables such as occupational categories or regional differences to streamline the model, these factors represent promising avenues for future research.
-For example, exploring the influence of specific professions or geographic contexts could reveal cultural and environmental interactions with socio-economic predictors.
+For example, exploring the influence of specific professions or geographic contexts could indicate cultural and environmental interactions with socio-economic predictors.
 Such investigations would refine current models and expand the understanding of happiness determinants.
@@
 
-Expanding the dataset to include broader samples across diverse regions or employing longitudinal data could improve generalizability and offer insights into how happiness evolves over time.
-Moreover, investigating the impact of external socio-economic factors, such as public policy changes or economic crises, could reveal macro-level influences on well-being.
+Expanding the dataset to include broader samples across diverse regions or employing longitudinal data could improve generalizability and offer findings into how happiness evolves over time.
+Moreover, investigating the impact of external socio-economic factors, such as public policy changes or economic crises, could indicate macro-level influences on well-being.
 
 Advancements in analytical methods, such as machine learning techniques, could uncover complex, non-linear relationships among variables that traditional regression models may overlook.
-For instance, examining interactions between age, income, and job satisfaction could illuminate critical periods and conditions for optimal well-being.
-
-These directions not only address the limitations of this study but also pave the way for a more comprehensive understanding of happiness in varied contexts, advancing both academic and policy-oriented research.
+For instance, examining interactions between age, income, and job satisfaction could illuminate essential periods and conditions for optimal well-being.
+
+These directions not only address the limitations of this study but also pave the way for a more detailed understanding of happiness in varied contexts, advancing both academic and policy-oriented research.
 
@@
 
-## The Value of Insights into Happiness Drivers
+## The Value of Findings into Happiness Drivers
 
@@
 These cleaning steps were essential for maintaining data integrity and ensuring that the analysis would provide meaningful and reliable results.
-By standardizing and filtering the data, the study could focus on valid and interpretable responses, minimizing noise and maximizing the quality of insights derived from the dataset.
+By standardizing and filtering the data, the study could focus on valid and interpretable responses, minimizing noise and maximizing the quality of findings derived from the dataset.
 
@@
 Our goal is to provide a robust analysis of the factors influencing individual happiness by designing a high-quality survey that captures data on key socio-economic and demographic variables.
-By addressing potential biases and ensuring representative sampling, this methodology aims to produce actionable insights within a manageable budget.
+By addressing potential biases and ensuring representative sampling, this methodology aims to produce actionable findings within a manageable budget.
 
@@
 
-This comprehensive methodology ensures reliable insights into the complex factors shaping individual happiness while laying the groundwork for future studies on well-being determinants.
+This detailed methodology ensures reliable findings into the complex factors shaping individual happiness while laying the groundwork for future studies on well-being determinants.
 
@@
 Completing the survey will take approximately 5–7 minutes.
-Thank you for your valuable participation!
+Thank you for your helpful participation!
 

### 2024-12-03 scripts/00-simulate_data.R

@@ -25,11 +25,14 @@ year <- rep(2016, n)  # All rows will have year = 2016
 # Generate marital status
 marital <- sample(c("Married", "Never married", "Divorced", "Widowed", "Separated"), n, replace = TRUE)
 
-# Generate number of children
-childs <- sample(0:5, n, replace = TRUE)
+# Generate number of children, influenced by marital status
+childs <- ifelse(marital == "Married", sample(0:5, n, replace = TRUE, prob = c(0.1, 0.2, 0.3, 0.2, 0.1, 0.1)),
+                 sample(0:3, n, replace = TRUE, prob = c(0.5, 0.3, 0.15, 0.05)))
 
-# Generate age values
-age <- round(runif(n, min = 18, max = 80))
+# Generate age values, slightly influenced by marital status
+age <- ifelse(marital == "Married", round(rnorm(n, mean = 40, sd = 10)), 
+              round(rnorm(n, mean = 30, sd = 8)))
+age <- pmin(pmax(age, 18), 80)  # Ensure age stays within 18-80
 
 # Generate degree values
 degree <- sample(c("High school", "Bachelor's", "Graduate", "No degree", "Less than high school",
@@ -38,15 +41,27 @@ degree <- sample(c("High school", "Bachelor's", "Graduate", "No degree", "Less t
 # Generate sex values
 sex <- sample(c("Male", "Female"), n, replace = TRUE)
 
-# Generate happiness values
-happy <- sample(c("Very happy", "Pretty happy", "Not too happy"), n, replace = TRUE)
+# Generate real income values, influenced by degree
+income_by_degree <- c("Less than high school" = 25000, "High school" = 35000, "Associate/junior college" = 45000,
+                      "Bachelor's" = 65000, "Graduate" = 85000, "No degree" = 30000)
+income_sd <- 15000
+realrinc <- round(rnorm(n, mean = unname(income_by_degree[degree]), sd = income_sd), 2)
+realrinc <- pmax(realrinc, 1000)  # Ensure income is non-negative
 
-# Generate job satisfaction values
-satjob <- sample(c("very satisfied", "moderately satisfied", "a little dissatisfied", "very dissatisfied"), n, replace = TRUE)
+# Generate job satisfaction, influenced by real income
+satjob <- cut(realrinc, breaks = c(-Inf, 30000, 60000, 90000, Inf),
[…]

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -10,112 +10,59 @@
 # Any other information needed? None 
 
 
-# Load necessary packages
+#### Workspace Setup ####
 library(dplyr)
 library(readr)
 library(arrow)
+library(testthat)
 
-# Load the simulated data
+#### Load the Simulated Data ####
 simulated_data <- read_parquet("data/00-simulated_data/predicting_happiness.parquet")
 
-# Define a test function
-check <- function(condition, success_msg, fail_msg) {
-  if (condition) {
-    message(success_msg)
-  } else {
-    stop(fail_msg)
-  }
-}
-
-#### Data Testing ####
+#### Begin Tests ####
 
 # Test 1: Check the number of rows
-check(
-  nrow(simulated_data) == 1000,
-  "Pass: The dataset contains exactly 1000 rows",
-  "Fail: The dataset does not contain 1000 rows"
-)
+test_that("Dataset contains exactly 1000 rows", {
+  expect_equal(nrow(simulated_data), 1000)
+})
 
 # Test 2: Check if all required columns exist
-required_columns <- c("year", "marital", "childs", "age", "degree", "sex", "happy", "satjob", "realrinc", "ballot")
-check(
-  all(required_columns %in% colnames(simulated_data)),
-  "Pass: All required columns are present",
-  paste("Fail: The following columns are missing: ", paste(setdiff(required_columns, colnames(simulated_data)), collapse = ", "))
-)
+test_that("All required columns are present", {
+  required_columns <- c("year", "marital", "childs", "age", "degree", "sex", "happy", "satjob", "realrinc", "ballot")
+  expect_true(all(required_columns %in% colnames(simulated_data)),
+              info = paste("Missing columns:", paste(setdiff(required_columns, colnames(simulated_data)), collapse = ", ")))
+})
 
-# Test 3: Check if year column is correctly set to 2016
-check(
-  all(simulated_data$year == 2016),
-  "Pass: All rows in the year column are set to 2016",
-  "Fail: Not all rows in the year column are set to 2016"
-)
+# Test 3: Check if year column is set to 2016
+test_that("Year column is set to 2016", {
+  expect_true(all(simulated_data$year == 2016))
+})
 
-# Test 4: Check if childs column is within the valid range (0 to 5)
-check(
-  all(simulated_data$childs >= 0 & simulated_data$childs <= 5, na.rm = TRUE),
-  "Pass: All values in the childs column are within the range 0 to 5",
-  "Fail: The childs column contains values outside the range 0 to 5"
-)
[…]

### 2024-12-03 scripts/03-clean_data.R

@@ -50,8 +50,6 @@ data <- data %>%
 # Check the cleaned data
 summary(data)
 
-# Save the cleaned data as a CSV file
-write_csv(data, "data/02-analysis_data/cleaned_happiness_data.csv")
 
 # Save the cleaned data as a Parquet file
 write_parquet(data, "data/02-analysis_data/cleaned_happiness_data.parquet")

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -10,94 +10,65 @@
 # Load required packages
 library(dplyr)
 library(readr)
+library(testthat)
 
 # Load data
 data <- read_csv("data/02-analysis_data/cleaned_happiness_data.csv")
 
-# Define a test function
-check <- function(condition, success_msg, fail_msg) {
-  if (condition) {
-    message(success_msg)
-  } else {
-    stop(fail_msg)
-  }
-}
+# Begin tests
+test_that("Dataset contains at least 100 rows", {
+  expect_true(nrow(data) >= 100, info = "Fail: The dataset contains fewer than 100 rows")
+})
 
-#### Data Testing ####
+test_that("All required columns are present", {
+  required_columns <- c("realrinc", "happy", "satjob", "childs", "age", "degree", "sex", "marital")
+  expect_true(all(required_columns %in% colnames(data)), 
+              info = paste("Fail: The following columns are missing: ", 
+                           paste(setdiff(required_columns, colnames(data)), collapse = ", ")))
+})
 
-# Test 1: Check the number of rows
-check(
-  nrow(data) >= 100,
-  "Pass: The dataset contains at least 100 rows",
-  "Fail: The dataset contains fewer than 100 rows"
-)
+test_that("All values in realrinc are non-negative", {
+  expect_true(all(data$realrinc >= 0, na.rm = TRUE), 
+              info = "Fail: realrinc contains negative values")
+})
 
-# Test 2: Check if all required columns exist
-required_columns <- c("realrinc", "happy", "satjob", "childs", "age", "degree", "sex", "marital")
-check(
-  all(required_columns %in% colnames(data)),
-  "Pass: All required columns are present",
-  paste("Fail: The following columns are missing: ", paste(setdiff(required_columns, colnames(data)), collapse = ", "))
-)
+test_that("All values in childs are within the valid range (0 to 8)", {
+  expect_true(all(data$childs >= 0 & data$childs <= 8, na.rm = TRUE), 
+              info = "Fail: childs contains invalid values")
+})
 
-# Test 3: Check if all values in realrinc are non-negative
-check(
-  all(data$realrinc >= 0, na.rm = TRUE),
-  "Pass: All values in realrinc are non-negative",
-  "Fail: realrinc contains negative values"
-)
+test_that("All values in age are within the valid range (18 to 120)", {
+  expect_true(all(data$age >= 18 & data$age <= 120, na.rm = TRUE), 
+              info = "Fail: age contains invalid values")
+})
 
[…]

### 2024-12-03 scripts/04-test_analysis_data.R
Update 04-test_analysis_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Test the data sets
 # Author: Shuheng (Jack) Zhou
-# Date: November 26 2024
+# Date: November 27 2024
 # Contact: shuhengzhou5@gmail.com
 # License: MIT
 # Pre-requisites: Run 02-download_data.R, 03-data_cleaning.R

### 2024-12-03 scripts/06-model_data.R
Update 06-model_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: To identify key factors influencing happiness levels using Bayesian Logistic Regression.
 # Author: Shuheng (Jack) Zhou
-# Date: November 26 2024
+# Date: November 27 2024
 # Contact: shuhengzhou5@gmail.com
 # License: MIT
 # Pre-requisites: Cleaned datasets should be available.

### 2024-12-03 scripts/05-exploratory_data_analysis.R
Update 05-exploratory_data_analysis.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Explore the analysis data
 # Author: Shuheng (Jack) Zhou
-# Date: November 26 2024
+# Date: November 27 2024
 # Contact: shuhengzhou5@gmail.com
 # License: MIT
 # Pre-requisites: Analysis data generated in 02-analysis_data

### 2024-12-03 scripts/01-test_simulated_data.R
Update 01-test_simulated_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Tests the structure and validity of the simulated happiness dataset.
 # Author: Shuheng (Jack) Zhou
-# Date: November 26 2024
+# Date: November 27 2024
 # Contact: shuhengzhou5@gmail.com
 # License: MIT
 # Pre-requisites: 

### 2024-12-03 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Cleans the raw happiness survey data from the General Social Survey (GSS) for analysis.
 # Author: Shuheng (Jack) Zhou
-# Date: November 26 2024
+# Date: November 27 2024
 # Contact: shuhengzhou5@gmail.com
 # License: MIT
 # Pre-requisites: Have raw data downloaded in the data file

### 2024-12-03 scripts/02-download_data.R
Update 02-download_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from GSS
 # Author: Shuheng (Jack) Zhou
-# Date: November 26 2024
+# Date: November 27 2024
 # Contact: shuhengzhou5@gmail.com
 # License: MIT
 # Pre-requisites: None

### 2024-12-03 scripts/00-simulate_data.R
Update 00-simulate_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Simulated the analysis dataset
 # Author: Shuheng (Jack) Zhou
-# Date: November 26 2024
+# Date: November 27 2024
 # Contact: shuhengzhou5@gmail.com
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
